### 2014-02-25 paper.tex
Adding empty paper

\documentclass[11pt]{article}
\usepackage{fancyvrb}
\usepackage{comment}
\usepackage[paper=letterpaper,margin=1.0in,includehead=false,includefoot=false]{geometry}

\newcommand{\cursor}{%
\begin{center}
\marginpar{\vskip 4pt\sc Cursor}
\begin{tabular*}{\linewidth}{c}
\hline
\end{tabular*}
\end{center}
}

\DefineVerbatimEnvironment{Code}{Verbatim}{fontsize=\footnotesize,xleftmargin=5pt}
\DefineVerbatimEnvironment{SemiCode}{Verbatim}{fontsize=\small,commandchars=\+\{\}}

\begin{document}

\title{Hello}
\author{Andy Gill, University of Kansas}
\maketitle

\section{...}

Hello

\end{document}

### 2014-02-25 paper.tex
Pulling in DSL text from 2012 proposal

@@
 
-\title{Hello}
+\title{Domain Specific Languages}
 \author{Andy Gill, University of Kansas}
@@
 
-\section{...}
+\section{A Domain Specific Language}
 
-Hello
+There are many ways to give a computer instructions.
+%
+%% "might" might sound better than "may"
+An electrical engineer might write a MATLAB program,
+a database administrator may write an SQL script,
+a hardware engineer may write in Verilog,
+and an accountant may write a spreadsheet
+with embedded formulas.
+%
+%% This sentence isn't clear, nor does it lead into the next sentence very well.
+%% I'd suggest expanding on this point to make it clearer.
+Aside from the difference in language, there is an
+important difference in {\em form\/} and {\em idiom\/}.
+%% Maybe you should emphasise "idiom" as well?
+%
+All of these examples use languages
+customized to the job at hand, and build computational
+requests in a form both familiar and productive
+for the programmer (though an accountant may
+not think of herself as a programmer.)
+All these examples are use of domain specific languages.
+
+A Domain Specific Language is a special purpose language,
+designed to encapsulate possible computations in a specific
+domain. Following our earlier examples of MATLAB, SQL,
+%% earlier examples of?
+Verilog, and spreadsheets, the domains would be scientific modeling,
+database queries and updates, hardware circuits, and financial computations, respectively.
+Considering SQL specifically, there is nothing SQL does that could not
+be done in Java or C, or any other general purpose programming
+language. SQL simply bundles the actions needed to
+interact with a database into a useable language,
+%% is useable the correct adjective here?  Java and C are useable languages too.
+and the language becomes the interface to communicate requests
+to the database engine.
+To pick a concrete example,
+consider the act of trying to list a dynamically updated leader-board
+for an online programming contest~\cite{Gill:11:CatchingSat}:
+\begin{Code}
+SELECT ROUND(SUM(s.Score)) as ss, t.TeamName FROM Solution s -- an aggregate score and team name
+   LEFT JOIN Team t ON SolutionTeam = TeamId                 -- where the team has the correct id
+   GROUP BY s.SolutionTeam                                   -- grouped by team name
+   ORDER BY ss DESC                                          -- ordered by score
+   LIMIT 20                                                  -- returning the first 20
+\end{Code}
+In a handful on lines, this query performs a complex
+database search, and some computation, finding
+the names and aggregate scores of the top 20 teams.
+
+There are two classes of DSL. (MORE)
+
+((Figure 1.))
+
+In this paper, we will examine Embedded DSL, focusing on
+
+\section{Embeded DSLs}
+
+((EXAMPLE of DSLs))
+
+Just a way of thinking about a library.
+
+What is an embedded DSL? We introduce it by looking
+at the history of $\mu$FP. Around 10 years after
+$\mu$FP, a language called Ruby emerged~\cite{Hutton:92:PhD,Hutton:93:RubyInterp};
+a $\mu$FP based on relations, with an even richer algebra,
+and at least one of the Ruby variants had a
+concrete DSL syntax, and could generate small circuits.
+Unfortunately, the rich algebras of relations
+were technically challenging to work with.
+Two independent Ruby implementations
+required a considerable maintenance of the DSL compiler,
+and both systems were later abandoned.
+
+The cost of maintaining a DSL outweighed the research
+discoveries being made. However, at this time,
+the idea of an EDSL~\cite{Hudak:96:BuildingEDSLs,Elliott:03:CompileDSEL-JFP} emerged.
+%
+An EDSL is a library in a host language
+that has the look, feel and semantics of its own language,
+customized to a specific problem domain.
+Haskell~\cite{Haskell98Book}, our functional language of choice, is a great host for EDSLs.
+%% Maybe these two sentences should be merged with a ``because of'' in the middle.
+Flexible overloading, a powerful type system, and lazy semantics facilitate this.
+
+The functional programming community took the ideas
+of EDSLs, which considerably lowered the costs of developing
+and maintaining a DSL, and revisited the $\mu$FP ideas,
+but in the context this time of functions.
+%% Should that be suffixed?
+This line of work, often suffixed with the word Lava,
+provided a number of implementations~\cite{Claessen:01:PhD,Singh:04:ReconfigLava,Sander:03:ForSyDe,ODonnell:02:Hydra}.
+Being based on functions rather than relations,
+they had a more straightforward algebras
+of rules. EDSLs were less expensive to maintain, and the research blossomed.
+But no system supported rewrites based on the published properties.
+
+Another observation to make regarding EDSLs is that
+there are two flavors:
+%% I don't like the use of ``First'' and ``Second'' in these bullet points.
+\begin{itemize}
+\item First, {\em DSLs that use a shallow embedding\/}, where values are computed with directly.
+The result of a computation in a shallow DSL is a value.
+\item Second, {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
+The result of a computation inside a deep DSL
+is a structure, not a value, and this structure can be used to compute a value,
+or be cross-compiled before being evaluated.
+\end{itemize}
+This is an important distinction. Historically, EDSLs have been shallow,
+and as such are simply a ways of structuring an API to a library. Deep EDSLs
+have the ability to {\em stage\/} code, that is executing a program
+can generate another program, much like the well-known YACC DSL,
+but at the cost of significantly restricting what forms of the DSL can
+generate valid output from.
+%% That sentence is a bit garbled.
+
+To allow us to be more specific, we now
+look at two case-studies:
+\begin{itemize}
+\item {\bf Kansas Lava} -- recent work by the PI on a hardware description DSL;
+\item and {\bf Sunroof} -- a DSL for calling and creating JavaScript, also by the PI.
+%% sunroof is your work too, right?
+\end{itemize}
+The unifying theme is that embedded DSLs can
+be pragmatic, productive and useful. We present
+these to allow us to make a technical argument that adding rewrite systems to
+DSLs will improve their usefulness by removing
+some of the inherent and outstanding shortcomings.
+
+\section{Deep Embeddings of DSLs}
+
+\section{Reification Tricks}
+
+The process of extracting a structure from a deeply embedded ESDL
+is called reification.
+
+\cursor{}
+
+ * running the description to get the AST
+
+\section{Use of Haskell’s type system for various things }
+
+ * expression data type 
+ * the phantom types trick 
+ * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
+ * usefulness of laziness 
+ * smart constructors ? 
+ * sharing ?
+
+%--------------------------------
+% CAREER12
+
+\section{Domain Specific Languages}
 

### 2014-03-02 paper.tex
Hacking the paper again.

@@
 \documentclass[11pt]{article}
+\usepackage{graphicx}
 \usepackage{fancyvrb}
@@
 
-\title{Domain Specific Languages}
+\title{Embedded Domain Specific Languages inside Functional Languages}
 \author{Andy Gill, University of Kansas}
@@
 consider the act of trying to list a dynamically updated leader-board
-for an online programming contest~\cite{Gill:11:CatchingSat}:
+for an online programming contest:
 \begin{Code}
@@
 
-There are two classes of DSL. (MORE)
+There are two fundimental types of Domain Specific Languages
+(Figure X).
+%
+The first, like the SQL example, is a first class language,
+with its own compiler or interpreter, and is often used in
+its own ecosystem. (Figure X, (1)) 
+All the examples mentioned so far fall
+into this categary. The primary difference between SQL and
+(say) Java is one of scope and focus, though sometimes
+DSLs grow to be as large are general purpose languages.
+%
+The other class of Domain Specific Languages are languages
+embeeded inside another hosting language. Such languages
+can have the look and feel of being their own languages,
+but leaverage the host language to provide an exisiting
+ecostructure and initial semantics. It is this second
+class of DSLs we are interested in, and is the subject of
+this paper.
 
-((Figure 1.))
+\begin{figure}
+((FIGURE ABOUT DSL))
 
-In this paper, we will examine Embedded DSL, focusing on
+\end{figure}
 
-\section{Embeded DSLs}
+\section{Embedded DSLs}
 
-((EXAMPLE of DSLs))
-
-Just a way of thinking about a library.
-
-What is an embedded DSL? We introduce it by looking
-at the history of $\mu$FP. Around 10 years after
-$\mu$FP, a language called Ruby emerged~\cite{Hutton:92:PhD,Hutton:93:RubyInterp};
-a $\mu$FP based on relations, with an even richer algebra,
-and at least one of the Ruby variants had a
-concrete DSL syntax, and could generate small circuits.
-Unfortunately, the rich algebras of relations
-were technically challenging to work with.
-Two independent Ruby implementations
-required a considerable maintenance of the DSL compiler,
-and both systems were later abandoned.
-
-The cost of maintaining a DSL outweighed the research
-discoveries being made. However, at this time,
-the idea of an EDSL~\cite{Hudak:96:BuildingEDSLs,Elliott:03:CompileDSEL-JFP} emerged.
-%
-An EDSL is a library in a host language
+An embedded DSL (EDSL) is a language inside a language.
+An EDSL implemented as a library in a host language
 that has the look, feel and semantics of its own language,
 customized to a specific problem domain.
-Haskell~\cite{Haskell98Book}, our functional language of choice, is a great host for EDSLs.
-%% Maybe these two sentences should be merged with a ``because of'' in the middle.
-Flexible overloading, a powerful type system, and lazy semantics facilitate this.
+Haskell~\cite{Haskell98Book}, our functional language of choice, is a great host for EDSLs
+because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
+The functional programming community has taken  the ideas
+of EDSLs, which considerably lowered the costs of developing
+and maintaining a DSL, and developed a number of DSL 
+which provide higher-level interfaces and abstractions for well-understood systems.
 
-The functional programming community took the ideas
-of EDSLs, which considerably lowered the costs of developing
-and maintaining a DSL, and revisited the $\mu$FP ideas,
-but in the context this time of functions.
-%% Should that be suffixed?
-This line of work, often suffixed with the word Lava,
-provided a number of implementations~\cite{Claessen:01:PhD,Singh:04:ReconfigLava,Sander:03:ForSyDe,ODonnell:02:Hydra}.
-Being based on functions rather than relations,
-they had a more straightforward algebras
-of rules. EDSLs were less expensive to maintain, and the research blossomed.
-But no system supported rewrites based on the published properties.
+\cursor{}
+
+\subsection{QuickCheck}
+
+As a first example of a EDSL, consider the challange of writing test cases.
+Or more specifically, writing the {\em properties\/} that test cases need to satisfy.
+
+\begin{Code}
+-- The reverse of a reversed list is itself
+prop_reverse (xs :: [Int]) = reverse (reverse xs) == xs
+\end{Code}
+
+\begin{Code}
+Prelude Test.QuickCheck> quickCheck prop_reverse 
++++ OK, passed 100 tests.
+\end{Code}
+
+((Go into my QC notes))
+
+\subsection{Lava}
+
+\section{Example HDL DSL: Kansas Lava}
+\label{sec:KansasLava}
+
+To take another example, consider describing hardware.
+Hardware description languages and functional languages have
+long enjoyed a fruitful partnership.
+{\bf Lava} is the name given to a class of Haskell DSLs
+that implement a function-based version of the hardware description
+language Ruby~\cite{Jones:90:Ruby,Hutton:93:RubyInterp}. Ruby, not to be confused with the
+modern programming language with the same name, was based
+on relations, not functions, and was inspired by
+the seminal work in $\mu$FP~\cite{Sheeran:84:muFP}.
+
+Kansas Lava~\cite{Gill:13:TypesKansasLava} is a Haskell-hosted DSL developed by the PI
+that follows the Lava line of research.
+It is a language for expressing gate-level circuits that can be compiled for FPGAs via VHDL.
+Haskell abstractions allow the programmer to work at
+a slightly higher level of abstraction, where the model
+is one of recursive components communicating via synchronized streams.
+Kansas Lava has been deployed for the generation of high-performance circuits for telemetry decoders,
+though the model used is general.
+It is a deep DSL, and therefore
+has the associated restrictions.
+
+\begin{figure}[!t]
+  \centering
+  \begin{minipage}{0.5\textwidth}
+    \centering
+    \includegraphics[width=0.8\textwidth]{images/Counter.pdf}
+  \end{minipage}\begin{minipage}{0.5\textwidth}
+     \centering
+\footnotesize\begin{Code}[fontsize=\tiny]
+entity counter is
+  port(rst : in std_logic;
+       clk : in std_logic;
+       clk_en : in std_logic;
+       restart : in std_logic;
+       inc : in std_logic;
+       output : out std_logic_vector(3 downto 0));
+end entity counter;
+architecture str of counter is
+  signal sig_2_o0 : std_logic_vector(3 downto 0);
+  ...
+begin
+  sig_2_o0 <= sig_5_o0 when (inc = '1')  else sig_6_o0;
+  sig_5_o0 <= std_logic_vector(...);
+  sig_6_o0 <= "0000" when (restart = '1') else sig_10_o0;
+  sig_10_o0_next <= sig_2_o0;
+  proc14 : process(rst,clk) is
+  begin
+    if rst = '1' then
+      sig_10_o0 <= "0000";
+    elsif rising_edge(clk) then
+      if (clk_en = '1') then
+        sig_10_o0 <= sig_10_o0_next;
+  ....
+end architecture;
+\end{Code}
+  \end{minipage}
+  \caption{{\tt counter} Schematic and VHDL Generated by Kansas Lava}
+  \label{fig:counter-picture}
+%  \vspace{-0.1in}
+\end{figure}
+
+As an example of Kansas Lava, consider:
+
+\begin{Code}
+
+counter :: (Rep a, Num a, Clock clk, sig ~ Signal clk) => sig Bool -> sig Bool -> sig a
+counter restart inc = loop
+   where reg = register 0 loop
+	 reg' = mux2 restart (0,reg)
+	 loop = mux2 inc (reg' + 1, reg')
+\end{Code}
+
+This circuit connects two multiplexers,
+an adder,
+and a \verb|register|
+to give a circuit that counts the number of
+clocked pulses on a signal \verb|inc|.
+The circuit takes two clocked signals,
+and returns a clocked signal that explicitly
+operates using the same clock, because they
+share the same type.
+Notice how the use of arithmetic is understated,
+but simply uses (via overloading) the
+standard syntax for addition; the {\tt Num}
+constraint allows this.
+Figure~\ref{fig:counter-picture} gives the
+circuit intended for this description.
+
+We can simulate sequential circuits with the
+same directness as the combinational functions we invoked.
+\begin{Code}
+GHCi> toSeq (cycle [True,False,False])
+T : F : F : T : F : F : T : F : F : ...
+GHCi> counter low (toSeq (cycle [True,False,False]))
+1 : 1 : 1 : 2 : 2 : 2 : 3 : 3 : 3 : ...
+\end{Code}
+
+We can also {\em reify\/} the circuit, into
+a VHDL program. This is the key advantage and the
+primary purpose of Kansas Lava. For example,
+if we reify the counter with a width of 4 bits, we generate
+the idiomatic but useable VHDL
+listed in Figure~\ref{fig:counter-picture}.
+
+As well as basic signal types,
+we can build circuits that operate on Haskell
+functions directly, provided the domain of the
+function is finite. We use the \verb|Rep|
+constraint to signify that we can enumerate
+all possible representable values in a type,
+giving the \verb|funMap| function.
+\begin{Code}
+funMap :: (Rep a, Rep b, Clock c, sig ~ Signal c) => (a -> Maybe b) -> sig a -> sig b
+\end{Code}
+The generated circuit is implemented using a ROM,
+and we can generate control logic
+directly in terms of Haskell functions
+and data-structures. As a example, consider
+a small ROM that stores the square of a
+value.
+\begin{Code}
+squareROM :: (Num a, Rep a, Clock c, sig ~ Signal c) => sig a -> sig a
+squareROM = funMap (\ x -> return (x * x))
+\end{Code}
+In this way, direct Haskell functions
+can be lifted into the \verb|Signal| world.
+Notice how the \verb|squareROM| function is
+not specific about size but is
+completely generic, only requiring the
+type of the argument stream
+to be representable as a number.
+
+This use of a Haskell DSL for expressing circuits
+is all well and good and {\em structural\/}.
+But how can Kansas Lava be utilized to
+describe more general forms of computation and parallelism?
+Unfortunately at this point the model breaks down
+to some degree. Programs can be written
+that generate specific components, like ALUs,
+but computation is more challenging to express
+in Kansas Lava and other deep DSLs.
+
+\subsection{Observations of Embedeed DSLs}
+
+As can be seen, EDSLs are simply a way of thinking about a library.
 
@@
 
-\cursor{}
-
  * running the description to get the AST

### 2014-03-02 paper.tex
Adding QC example

@@
 because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
-The functional programming community has taken  the ideas
+
+As an example of Haskell, consider reversing a list in Haskell
+\begin{Code}
+reverse :: [a] -> [a]
+reverse []     = []
+reverse (x:xs) = reverse xs ++ [x]
+\end{Code}
+
+This is the complete defintion of reverse: reverse reverses any type of list (the first line);
+the reverse of an empty list, written \verb|[]|, is an empty list;
+and the reverse of an non-empty list is the reverse of the tail of a linked-list,
+appended to the front of the list.
+
+Using this consise syntax, Haskell specifically and the functional programming
+community in general have taken the ideas
 of EDSLs, which considerably lowered the costs of developing
-and maintaining a DSL, and developed a number of DSL 
+and maintaining a DSL, and developed many, many of DSL 
 which provide higher-level interfaces and abstractions for well-understood systems.
-
-\cursor{}
 
@@
 
+\verb|prop_reverse| is itself a regular Haskell function,
+that takes a list of Int, and returns a boolean, based
+on the validity of what is being proposed, specifically
+that is a two reverses cancel each other out. 
+Here is the neat part -- \verb|prop_reverse| is {\bf also\/} a
+domain specific statement, and as such can also be considered
+a sub-language inside of Haskell itself.  This style
+of using function, in this case function with names
+prefixed with \verb|prop_|, taking a number of typed
+arguments, and returning a conditional. The property
+written in Haskell is also an Embeeded Domain specific
+language for properties.
+
+We can run our EDSL, using a function called \verb|quickCheck|:
 \begin{Code}
@@
 \end{Code}
+By running \verb|quickCheck| with our explicit and specific property,
+we execute our ESDL inside Haskell. The quickCheck function
+generates 100 test cases for our property, and exectutes
+them on the fly. If they all hold, then the system prints
+a message reflecting this.
+
+In turns out that this sort of mini-language is really useful in practice.
 
 ((Go into my QC notes))
+
+\cursor{}
 

### 2014-03-04 paper.tex
Towards explaining deep embeddings

@@
 
-\subsection{QuickCheck}
+\subsection{Example EDSL: QuickCheck}
 
@@
 
-\cursor{}
-
-\subsection{Lava}
-
-\section{Example HDL DSL: Kansas Lava}
-\label{sec:KansasLava}
+\section{Example EDSL: Kansas Lava}\label{sec:KansasLava}
 
@@
 that follows the Lava line of research.
-It is a language for expressing gate-level circuits that can be compiled for FPGAs via VHDL.
+Kansas Lava is a language for expressing gate-level circuits.
 Haskell abstractions allow the programmer to work at
@@
 though the model used is general.
-It is a deep DSL, and therefore
-has the associated restrictions.
+
+As an example of Kansas Lava, consider:
+
+\begin{Code}
+
+counter :: (Rep a, Num a, Clock clk, sig ~ Signal clk) => sig Bool -> sig Bool -> sig a
+counter restart inc = loop
+   where reg = register 0 loop
+	 reg' = mux2 restart (0,reg)
+	 loop = mux2 inc (reg' + 1, reg')
+\end{Code}
+
+This circuit connects two multiplexers (\verb|mux2|),
+an adder,
+and a \verb|register|
+to give a circuit that counts the number of
+clocked pulses on a signal \verb|inc|.
+The circuit takes two clocked signals,
+and returns a clocked signal that explicitly
+operates using the same clock, because they
+share the same type.
+The use of arithmetic is understated,
+but simply uses (via overloading) the
+standard syntax for addition; the {\tt Num}
+constraint allows this.
+Figure~\ref{fig:counter-picture} gives the
+circuit intended for this description.
+
+We can simulate sequential circuits with the
+same directness as the combinational functions we invoked.
+\begin{Code}
+GHCi> toSeq (cycle [True,False,False])
+T : F : F : T : F : F : T : F : F : ...
+GHCi> counter low (toSeq (cycle [True,False,False]))
+1 : 1 : 1 : 2 : 2 : 2 : 3 : 3 : 3 : ...
+\end{Code}
+
+As well as basic signal types,
+we can build circuits that operate on Haskell
+functions directly, provided the domain of the
+function is finite. We use the \verb|Rep|
+constraint to signify that we can enumerate
+all possible representable values in a type,
+giving the \verb|funMap| function.
+\begin{Code}
+funMap :: (Rep a, Rep b, Clock c, sig ~ Signal c) => (a -> Maybe b) -> sig a -> sig b
+\end{Code}
+The generated circuit is implemented using a ROM,
+and we can generate control logic
+directly in terms of Haskell functions
+and data-structures. As a example, consider
+a small ROM that stores the square of a
+value.
+\begin{Code}
+squareROM :: (Num a, Rep a, Clock c, sig ~ Signal c) => sig a -> sig a
+squareROM = funMap (\ x -> return (x * x))
+\end{Code}
+In this way, direct Haskell functions
+can be lifted into the \verb|Signal| world.
+Notice how the \verb|squareROM| function is
+not specific about size but is
+completely generic, only requiring the
+type of the argument stream
+to be representable as a number.
+
+\subsection{Observations of Embedeed DSLs}
+
+As can be seen, EDSLs are simply a way of thinking about a library
+of provided functions, often called combinators, because they combine
+their arguments into terms inside the DSL lanuage.
+
+(((MORE))
+
+Another observation to make regarding EDSLs is that
+there are two flavors:
+%% I don't like the use of ``First'' and ``Second'' in these bullet points.
+\begin{itemize}
+\item First, {\em DSLs that use a shallow embedding\/}, where values are computed with directly.
+The result of a computation in a shallow DSL is a value.
+\item Second, {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
+The result of a computation inside a deep DSL
+is a structure, not a value, and this structure can be used to compute a value,
+or be cross-compiled before being evaluated.
+\end{itemize}
+This is an important distinction. Historically, EDSLs have been shallow,
+and as such are simply a ways of structuring an API to a library. Deep EDSLs
+have the ability to {\em stage\/} code, that is executing a program
+can generate another program, much like the well-known YACC DSL,
+but at the cost of significantly restricting what forms of the DSL can
+generate valid output from.
+%% That sentence is a bit garbled.
+
+The unifying theme is that embedded DSLs can
+be pragmatic, productive and useful. We present
+these to allow us to make a technical argument that adding rewrite systems to
+DSLs will improve their usefulness by removing
+some of the inherent and outstanding shortcomings.
+
+\section{Deep Embeddings of DSLs}
+
+A deeply embeeded DSL can be ...
+
+\subsection{How to extract a deep embedding}
+
+The basis of
+
+\subsection{Example: Deep EDSL for Lava}
+
+\section{Reification Tricks}
+
+The process of extracting a structure from a deeply embedded ESDL
+is called reification.
+
+ * running the description to get the AST
+
+\section{Use of Haskell’s type system for various things }
+
+ * expression data type 
+ * the phantom types trick 
+ * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
+ * usefulness of laziness 
+ * smart constructors ? 
+ * sharing ?
+
+%--------------------------------
+% CAREER12
+
+\section{Domain Specific Languages}
 
@@
 
-As an example of Kansas Lava, consider:
-
-\begin{Code}
-
-counter :: (Rep a, Num a, Clock clk, sig ~ Signal clk) => sig Bool -> sig Bool -> sig a
-counter restart inc = loop
-   where reg = register 0 loop
-	 reg' = mux2 restart (0,reg)
-	 loop = mux2 inc (reg' + 1, reg')
-\end{Code}
-
-This circuit connects two multiplexers,
-an adder,
-and a \verb|register|
-to give a circuit that counts the number of
-clocked pulses on a signal \verb|inc|.
-The circuit takes two clocked signals,
-and returns a clocked signal that explicitly
-operates using the same clock, because they
-share the same type.
-Notice how the use of arithmetic is understated,
-but simply uses (via overloading) the
-standard syntax for addition; the {\tt Num}
-constraint allows this.
-Figure~\ref{fig:counter-picture} gives the
-circuit intended for this description.
-
-We can simulate sequential circuits with the
-same directness as the combinational functions we invoked.
-\begin{Code}
-GHCi> toSeq (cycle [True,False,False])
-T : F : F : T : F : F : T : F : F : ...
-GHCi> counter low (toSeq (cycle [True,False,False]))
-1 : 1 : 1 : 2 : 2 : 2 : 3 : 3 : 3 : ...
-\end{Code}
-
 We can also {\em reify\/} the circuit, into
@@
 listed in Figure~\ref{fig:counter-picture}.
-
-As well as basic signal types,
-we can build circuits that operate on Haskell
-functions directly, provided the domain of the
-function is finite. We use the \verb|Rep|
-constraint to signify that we can enumerate
-all possible representable values in a type,
-giving the \verb|funMap| function.
-\begin{Code}
-funMap :: (Rep a, Rep b, Clock c, sig ~ Signal c) => (a -> Maybe b) -> sig a -> sig b
-\end{Code}
-The generated circuit is implemented using a ROM,
-and we can generate control logic
-directly in terms of Haskell functions
-and data-structures. As a example, consider
-a small ROM that stores the square of a
-value.
-\begin{Code}
-squareROM :: (Num a, Rep a, Clock c, sig ~ Signal c) => sig a -> sig a
-squareROM = funMap (\ x -> return (x * x))
-\end{Code}
-In this way, direct Haskell functions
-can be lifted into the \verb|Signal| world.
-Notice how the \verb|squareROM| function is
-not specific about size but is
-completely generic, only requiring the
-type of the argument stream
-to be representable as a number.
 
@@
 
-\subsection{Observations of Embedeed DSLs}
-
-As can be seen, EDSLs are simply a way of thinking about a library.
-
-Another observation to make regarding EDSLs is that
-there are two flavors:
-%% I don't like the use of ``First'' and ``Second'' in these bullet points.
-\begin{itemize}
-\item First, {\em DSLs that use a shallow embedding\/}, where values are computed with directly.
-The result of a computation in a shallow DSL is a value.
-\item Second, {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
-The result of a computation inside a deep DSL
-is a structure, not a value, and this structure can be used to compute a value,
-or be cross-compiled before being evaluated.
-\end{itemize}
-This is an important distinction. Historically, EDSLs have been shallow,
-and as such are simply a ways of structuring an API to a library. Deep EDSLs
-have the ability to {\em stage\/} code, that is executing a program
-can generate another program, much like the well-known YACC DSL,
-but at the cost of significantly restricting what forms of the DSL can
-generate valid output from.
-%% That sentence is a bit garbled.
-
-To allow us to be more specific, we now
-look at two case-studies:
-\begin{itemize}
-\item {\bf Kansas Lava} -- recent work by the PI on a hardware description DSL;
-\item and {\bf Sunroof} -- a DSL for calling and creating JavaScript, also by the PI.
-%% sunroof is your work too, right?
-\end{itemize}
-The unifying theme is that embedded DSLs can
-be pragmatic, productive and useful. We present
-these to allow us to make a technical argument that adding rewrite systems to
-DSLs will improve their usefulness by removing
-some of the inherent and outstanding shortcomings.
-
-\section{Deep Embeddings of DSLs}
-
-\section{Reification Tricks}
-
-The process of extracting a structure from a deeply embedded ESDL
-is called reification.
-
- * running the description to get the AST
-
-\section{Use of Haskell’s type system for various things }
-
- * expression data type 
- * the phantom types trick 
- * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
- * usefulness of laziness 
- * smart constructors ? 
- * sharing ?
-
-%--------------------------------
-% CAREER12
-
-\section{Domain Specific Languages}
-
 \end{document}

### 2014-03-06 paper.tex
Adding text about Haskell.

@@
 \end{figure}
+
+\section{Haskell Primer}
+
+\section{Haskell}
+
+Haskell is the premier pure functional programming language.
+Haskell supports many forms of abstraction, and provides
+a robust foundation for building Domain Specific Languages (DSLs).
+In this section, we give a terse
+introduction to Haskell,
+sufficient to make this paper self-contained.
+
+Haskell is all about {\em types\/}. Types in Haskell, like
+types in other languages, are constraining summaries of structural values.
+For example, in Haskell \verb|Bool| is the type of the values
+\verb|True| and \verb|False|, \verb|Int| is the type of machine-sized
+words, \verb|Double| is the type of double precision floating
+point values; and this list goes on in the same manner as
+\verb|C|, \verb|C++|, \verb|Java| and other traditional languages.
+All these type names in Haskell start with an upper-case letter.
+
+On top of these basic types, Haskell has two syntactical forms for expressing
+compound types.
+First, pairs, triples and larger structures can be written using tuple syntax,
+comma separated types inside parenthesis.
+So |(Int,Bool)| is structure with both an |Int| and a |Bool| component.
+Second, lists have a syntactical shortcut, using square brackets.
+So |[Int]| is a list of |Int|.
+
+Haskell also has other container types. A container
+that {\em may\/} contain one |Int| has the type
+\verb|Maybe Int|
+which is read |Maybe| of |Int|.
+These container names also start with upper-case letters.
+Types can be nested to any depth. For example, we can have a \verb|[(Maybe (Int,Bool))]|,
+read as list of |Maybe| of (|Int| and |Bool|).
+
+Polymorphic values, which are analogous to the type |Object| in Java,
+or |void*| pointers in C, are expressed using lower-case letters.
+These polymorphic values can have constraints expressed over them,
+using the Haskell equivalent of an object hierarchy.
+Finally, a Haskell function that takes a list, and returns a list
+is written as using an arrow: |[a] -> [a]|.
+
+We can now give an example of a Haskell function.%, the function \verb|sort|.
+\begin{Code}
+
+sort :: (Ord a) => [a] -> [a]
+sort []     = []
+sort (x:xs) = sort before ++ [x] ++ sort after
+  where
+        before = filter (<= x) xs
+        after  = filter (> x) xs
+
+\end{Code}
+This function sorted a list, using a variant of quicksort in which the pivot is
+the front of the list.
+\begin{itemize}
+\item The first line is the type for |sort|. This is $\forall$|a|, such that
+|a| can be |Ord|ered (admits comparisons like |<=|), the function
+takes and return a list of such |a|'s.
+\item The second line says that an empty list is already sorted.
+\item The remaining lines state that a (non-empty) list can be
+sorted by taking the first and rest of the list (called |x| and |xs|, respectively),
+and sorting the values before this pivot and after this pivot,
+and concatenating theses intermediate values together.
+\item Finally, intermediate values can be named using the |where| syntax;
+in this case the values of |before| and |after|.
+\end{itemize}
+
+\pagebreak
+Haskell is a concise and direct language.
+Structures in Haskell are described using types, constructed
+and deconstructed, but never updated. The entire language
+functions by chaining together these structural processors,
+which ultimately take input, and produce output. Side-effects
+are described using a |do|-notation, for example:
+
+\begin{Code}
+
+main :: IO ()
+main = do
+  putStrLn "Hello"
+  xs <- getLine
+  print xs
+
+\end{Code}
+
+In this example a {\em value\/} called |main| uses the |do|-notation to describe
+an interaction with a user. Actually, the |do|-notation captures
+this as a structure called a Monad; purity is not compromised. For more details
+about how |do|-notation and Monads can provide an effectful interface
+inside a pure language like Haskell, see~\cite{SPJ:93:IFP}. For the
+purposes of Kansas Lava, |do|-notation is a way of providing syntax
+and structure that looks like interaction.
 

### 2014-03-06 paper.tex
Hacking paper

@@
 
-\pagebreak
 Haskell is a concise and direct language.
 Structures in Haskell are described using types, constructed
-and deconstructed, but never updated. The entire language
+and deconstructed, but never updated.
+
+(( ABOUT DATA Construct ))
+
+\begin{Code}
+
+data Maybe where
+  Nothing ::      Maybe a
+  Just    :: a -> Maybe a
+
+\end{Code}
+
+The entire language
 functions by chaining together these structural processors,
@@
 inside a pure language like Haskell, see~\cite{SPJ:93:IFP}. For the
-purposes of Kansas Lava, |do|-notation is a way of providing syntax
+purposes of this article, |do|-notation is a way of providing syntax
 and structure that looks like interaction.
@@
 
+Compositionally
+Combining elements into more complex ones should be easy and natural.
+Abstraction
+The user shouldn’t have to know (or be allowed to exploit) the underlying implementation of your types.
+
 (((MORE))
 
-Another observation to make regarding EDSLs is that
-there are two flavors:
-%% I don't like the use of ``First'' and ``Second'' in these bullet points.
-\begin{itemize}
-\item First, {\em DSLs that use a shallow embedding\/}, where values are computed with directly.
+There are two flavors of EDSLs.
+The most common flavor are
+{\em DSLs that use a shallow embedding\/}, where values are computed with directly.
 The result of a computation in a shallow DSL is a value.
-\item Second, {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
+But there is another class of DSLs, 
+specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
 The result of a computation inside a deep DSL
@@
 or be cross-compiled before being evaluated.
-\end{itemize}
+
 This is an important distinction. Historically, EDSLs have been shallow,
@@
 The unifying theme is that embedded DSLs can
-be pragmatic, productive and useful. We present
-these to allow us to make a technical argument that adding rewrite systems to
-DSLs will improve their usefulness by removing
-some of the inherent and outstanding shortcomings.
+be pragmatic, productive and useful.
 
@@
 
-A deeply embeeded DSL can be ...
+A deeply embeeded DSL is a DSL than can have ???.
+To make this concreate, consider a DSL for arithmetic,
+with addition, subtraction, multiplcation, and constants.
+We want to be able to {\bf run\/} this DSL. For a shallow
+embedding this is trival - we just use the built in 
+arithmetic. A deep embedding is where things get
+interesting. Consider a data-type for our arithmetic.
 
-\subsection{How to extract a deep embedding}
+\begin{Code}
+data E where
+ Lit :: Integer  -> E
+ Add :: E -> E -> E
+ Sub :: E -> E -> E
+ Mul :: E -> E -> E
+ deriving Eq
+\end{Code}
 
-The basis of
+Now we overload the arithemtic to use this E datatype;
+in Haskell Num is our overloading for integeral arithmetic.
+
+\begin{Code}
+instance Num E where
+  e1 + e2 = Add e1 e2
+  ...
+
+\end{Code}
+
+Now, if we build expressions of type E, we can
+observe the structure of the computation.
+\begin{SemiCode}
+GHCi> 1 + 2 * 3
+Mul (Add (Lit 1) (Lit 2)) (Lit 3)
+\end{SemiCode}
+
+With deep embeddings, it is common to also
+write a run function, that computes the structure
+of a catured computation, given a simple value.
+\begin{Code}
+run :: E -> Int
+run (...)
+\end{Code}
+
+About running the code.
+
+\subsection{How to extract a deep embedding from a Function}
+
+Expressing function calls in terms of constructors,  and
+building expression trees is a gimic. THere are entire
+systems build on the idea of building structures 
+in principaled ways, for example JHDL~\cite{..}, but
+we can do much more. With careful construction,
+we can capture function defintions,
+and other synatically structuruals,
+directly from a deep embedding. It is at this
+point, the idea of capturing code,
+the using the captured code to execute code
+on a different target becomes possible.
+
+\begin{Code}
+
+f :: E -> E
+f x = x + 1
+
+\end{Code}
+
+Here we have a function that acts over our new type
+\verb|E|, and returns a new \verb|E|. How can we capture
+this function.
+The trick is to invent a unique E, and pass it as the argument
+to \verb|f|.
+
+\begin{Code}
+data E where
+  Lit :: Integer -> E
+  ...
+  Var :: String -> E    -- new constructor
+\end{Code}
+
+\begin{Code}
+-- Just running the function
+> f 4
+Add (Lit 4) (Lit 1)
+-- reifing the function, using our unique E ``Var''.
+> f (Var "x")
+Add (Var "x") (Lit 1)   -- reified verision of the function
+\end{Code}
+
+This is remarkabile. We're run a function with 
+a dummy argument (called the protypical argument)
+and extracted the body of the function.
+
+The obvious questions are does this trick used here scale,
+and what are the limitations? The trick has
+been used on may large examples, including
+generating large telemerty circuits, 
+and (( .. feldspar )). It is considered a
+stardard pattern in the functional programming
+community, analogoues to the OO patterns
+enumerated in the gang of four book~\cite{..}.
+The trick is made all the more appealing
+because we can use operator overloading.
+But the trick does has serious limitations.
+
+The basis of a Deep EDSL is one of constructiveness.
+The aim is to construct a structure, then
+use that structure that was previously implicit.
+Figure sumurizes the state of the art with
+deeply embeeded reification
+
+\begin{verbatim}
+Expressions             Natural Fit
+Functions               The trick
+local bindings          Yes, using observable sharing
+internal functions      Yes, using extension of OS
+do-statements           Yes, using monadic reification
+control flow            Not directly, can simulate
+\end{verbatim}
+
+However, the trick breaks down on control flow,
+which is not constructive, but instead requires
+answers.
 
 \subsection{Example: Deep EDSL for Lava}
+
+Lava programs are written as equations of recusive bindings.
 

### 2014-03-13 paper.tex
wibbles with english
Fixing some errors, more text.

@@
 
-A deeply embeeded DSL is a DSL than can have ???.
-To make this concreate, consider a DSL for arithmetic,
-with addition, subtraction, multiplcation, and constants.
+A deeply embedded DSL is a DSL than can have ???.
+To make this concrete, consider a DSL for arithmetic,
+with addition, subtraction, multiplication, and constants.
 We want to be able to {\bf run\/} this DSL. For a shallow
@@
 
+About 3 main tricks; functions, recursive values, and statements.
+
 \subsection{How to extract a deep embedding from a Function}
@@
 > f (Var "x")
-Add (Var "x") (Lit 1)   -- reified verision of the function
+Add (Var "x") (Lit 1)   -- reified version of the function
 \end{Code}
 
-This is remarkabile. We're run a function with 
+This is remarkable. We're run a function with 
 a dummy argument (called the protypical argument)
 and extracted the body of the function.
+
+About where is used.
+
+\subsection{How to spot a loop}
+
+Lava programs are written as equations of recursive bindings.
+If we attempt to build a deep embedding of Lava directly,
+we will get into a infinite cycle. In order to illustrate
+the challenge, we will build a deep embedding of Lava,
+see where it goes wrong, and fix it using a technique called
+observable sharing.
+
+First we need a structure for our Lava Language.
+\begin{Code}
+
+data Signal where
+  Register :: a -> Signal a                      -> Signal a
+  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal a
+  Var      :: String                             -> Signal a -- the trick
+
+mux2 :: ...
+mux2 = mux2
+
+toSeq :: a -> Signal a
+toSeq = ...
+\end{Code}
+
+\section{Reification Tricks}
 
@@
 
-However, the trick breaks down on control flow,
+The Deep EDSL trick breaks down on control flow,
 which is not constructive, but instead requires
-answers.
-
-\subsection{Example: Deep EDSL for Lava}
-
-Lava programs are written as equations of recusive bindings.
-
-\section{Reification Tricks}
+directly
 

### 2014-03-13 paper.tex
Starting monadic reification

@@
 
-There are two fundimental types of Domain Specific Languages
+There are two fundamental types of Domain Specific Languages
 (Figure X).
@@
 The other class of Domain Specific Languages are languages
-embeeded inside another hosting language. Such languages
+embedded inside another hosting language. Such languages
 can have the look and feel of being their own languages,
-but leaverage the host language to provide an exisiting
-ecostructure and initial semantics. It is this second
+but leverage the host language to provide an existing
+eco-structure and initial semantics. It is this second
 class of DSLs we are interested in, and is the subject of
@@
 toSeq = ...
+
+instance Signal Sig where {...}
+
 \end{Code}
+
+\subsection{How to spot an imperative}
+
+Sometimes, a list of actions is the best way to express what you want to do.
+In Haskell, the \verb|do|-notation is used to chain together imperative actions.
+To give an example,
 
@@
 
-The obvious questions are does this trick used here scale,
+The obvious questions are do this tricks used here scale,
 and what are the limitations? The trick has
@@
 use that structure that was previously implicit.
-Figure sumurizes the state of the art with
-deeply embeeded reification
+Figure summarizes the state of the art with
+deeply embedded reification
 

### 2014-03-13 paper.tex
Fixing Haskell primer

@@
 language. SQL simply bundles the actions needed to
-interact with a database into a useable language,
+interact with a database into a useable and productive package,
 %% is useable the correct adjective here?  Java and C are useable languages too.
@@
 All the examples mentioned so far fall
-into this categary. The primary difference between SQL and
+into this category. The primary difference between SQL and
 (say) Java is one of scope and focus, though sometimes
@@
 \begin{figure}
+
+\vskip 1in        
 ((FIGURE ABOUT DSL))
@@
 
-\section{Haskell}
-
-Haskell is the premier pure functional programming language.
-Haskell supports many forms of abstraction, and provides
-a robust foundation for building Domain Specific Languages (DSLs).
+An Embedded DSL (EDSL) is a language inside a language.
+Haskell~\cite{Haskell98Book}, the premier pure functional programming language, is a great host for EDSLs
+because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
 In this section, we give a terse
 introduction to Haskell, 
-sufficient to make this paper self-contained.
+sufficient to make this article self-contained. This section was
+adapted from the Haskell primer given in~\cite{?}.
 
@@
 comma separated types inside parenthesis.
-So |(Int,Bool)| is structure with both an |Int| and a |Bool| component.
+So \verb|(Int,Bool)| is structure with both an \verb|Int| and a \verb|Bool| component.
 Second, lists have a syntactical shortcut, using square brackets.
-So |[Int]| is a list of |Int|.
+So \verb|[Int]| is a list of \verb|Int|.
 
 Haskell also has other container types. A container
-that {\em may\/} contain one |Int| has the type
+that {\em may\/} contain one \verb|Int| has the type
 \verb|Maybe Int|
-which is read |Maybe| of |Int|.
+which is read \verb|Maybe| of \verb|Int|.
 These container names also start with upper-case letters.
 Types can be nested to any depth. For example, we can have a \verb|[(Maybe (Int,Bool))]|,
-read as list of |Maybe| of (|Int| and |Bool|).
+read as list of \verb|Maybe| of (\verb|Int| and \verb|Bool|).
 
-Polymorphic values, which are analogous to the type |Object| in Java,
-or |void*| pointers in C, are expressed using lower-case letters.
+Polymorphic values, which are analogous to the type \verb|Object| in Java,
+or \verb|void*| pointers in C, are expressed using lower-case letters.
 These polymorphic values can have constraints expressed over them,
@@
 Finally, a Haskell function that takes a list, and returns a list
-is written as using an arrow: |[a] -> [a]|.
+is written as using an arrow: \verb|[a] -> [a]|.
 
@@
 This function sorted a list, using a variant of quicksort in which the pivot is
-the front of the list.
+the first element of the list.
 \begin{itemize}
-\item The first line is the type for |sort|. This is $\forall$|a|, such that
-|a| can be |Ord|ered (admits comparisons like |<=|), the function
-takes and return a list of such |a|'s.
+\item The first line is the type for \verb|sort|. This is $\forall$\verb|a|, such that
+\verb|a| can be \verb|Ord|ered (admits comparisons like \verb|<=|), the function
+takes and return a list of such \verb|a|'s.
 \item The second line says that an empty list is already sorted.
 \item The remaining lines state that a (non-empty) list can be
-sorted by taking the first and rest of the list (called |x| and |xs|, respectively),
+sorted by taking the first and rest of the list (called \verb|x| and \verb|xs|, respectively),
 and sorting the values before this pivot and after this pivot,
 and concatenating theses intermediate values together.
-\item Finally, intermediate values can be named using the |where| syntax;
-in this case the values of |before| and |after|.
+\item Finally, intermediate values can be named using the \verb|where| syntax;
+in this case the values of \verb|before| and \verb|after|.
 \end{itemize}
@@
 Haskell is a concise and direct language.
-Structures in Haskell are described using types, constructed
-and deconstructed, but never updated.
-
-(( ABOUT DATA Construct ))
-
+Structures in Haskell are denoted using types, constructed
+and deconstructed, but never updated. For example, the \verb|Maybe| type
+can been defined using two constructors, \verb|Nothing|, and \verb|Just|.
 \begin{Code}
@@
 \end{Code}
+\verb|Nothing| is a verb|Maybe| of anything, \verb|Just|, with an argument,
+is a \verb|Maybe| with the type of the argument. These constructors can be
+used to construct and deconstruct structures, but there is never any updating;
+all structures as immutable.
 
-The entire language
-functions by chaining together these structural processors,
-which ultimately take input, and produce output. Side-effects
-are described using a |do|-notation, for example:
+It is possible to give specific types extra powers, like equality and comparison,
+using the class based overloading system. In the case of \verb|Maybe|, we
+can give the \verb|Maybe| type the ability to test for equality, using an
+instance.
+\begin{Code}
+instance Eq a => Eq (Maybe a) where        
+   Just a  == Just b  = a == b
+   Nothing == Nothing = True
+   _       == _       = False
+\end{Code}
+
+This states that for any type that can be testing for equality,
+we can also check \verb|Maybe| at the same type. We take the \verb|Maybe|
+apart, using pattern matching on \verb|Just|, to check the internal value.a
+
+In Haskell, Side-effects such as writing to the screen
+or reading the keyboard are described using a \verb|do|-notation, for example:
 
@@
 
-In this example a {\em value\/} called |main| uses the |do|-notation to describe
-an interaction with a user. Actually, the |do|-notation captures
+In this example a {\em value\/} called \verb|main| uses the \verb|do|-notation to describe
+an interaction with a user. Actually, the \verb|do|-notation captures
 this as a structure called a Monad; purity is not compromised. For more details
-about how |do|-notation and Monads can provide an effectful interface
+about how \verb|do|-notation and Monads can provide an effectful interface
 inside a pure language like Haskell, see~\cite{SPJ:93:IFP}. For the
-purposes of this article, |do|-notation is a way of providing syntax
-and structure that looks like interaction.
+purposes of this article, \verb|do|-notation is a way of providing syntax
+and structure that looks like interaction. There are many tutorials
+on Haskell, but the Haskell website, \verb|haskell.org| is a good starting point
+for further reading.
 

### 2014-03-13 paper.tex
Basic QC complete

@@
 
-An embedded DSL (EDSL) is a language inside a language.
-An EDSL implemented as a library in a host language
-that has the look, feel and semantics of its own language,
+An EDSL is a library in a host language which has the look, feel and semantics of its own language,
 customized to a specific problem domain.
-Haskell~\cite{Haskell98Book}, our functional language of choice, is a great host for EDSLs
-because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
-
-As an example of Haskell, consider reversing a list in Haskell
-\begin{Code}
-reverse :: [a] -> [a]
-reverse []     = []
-reverse (x:xs) = reverse xs ++ [x]
-\end{Code}
-
-This is the complete defintion of reverse: reverse reverses any type of list (the first line);
-the reverse of an empty list, written \verb|[]|, is an empty list;
-and the reverse of an non-empty list is the reverse of the tail of a linked-list,
-appended to the front of the list.
-
-Using this consise syntax, Haskell specifically and the functional programming
+Using Haskell's concise syntax, Haskell specifically and the functional programming
 community in general have taken the ideas
@@
 
-\subsection{Example EDSL: QuickCheck}
+We look at two examples of DSLs, one for automatically generating test cases for software testing,
+and a second for specifying hardware circuit behaviors.
 
-As a first example of a EDSL, consider the challange of writing test cases.
+\subsection{Example EDSL: QuickCheck Properties}
+
+As a first example of a EDSL, consider the challenge of writing test cases.
 Or more specifically, writing the {\em properties\/} that test cases need to satisfy.
@@
 \begin{Code}
--- The reverse of a reversed list is itself
-prop_reverse (xs :: [Int]) = reverse (reverse xs) == xs
+-- The reverse of a reverse'd list is itself
+prop_reverse_twice (xs :: [Int]) = reverse (reverse xs) == xs
 \end{Code}
 
-\verb|prop_reverse| is itself a regular Haskell function,
+\verb|prop_reverse_twice| is a regular Haskell function,
 that takes a list of Int, and returns a boolean, based
@@
 that is a two reverses cancel each other out. 
-Here is the neat part -- \verb|prop_reverse| is {\bf also\/} a
+Here is the neat part -- \verb|prop_reverse_twice| is {\bf also\/} a
 domain specific statement, and as such can also be considered
 a sub-language inside of Haskell itself.  This style
-of using function, in this case function with names
+of using functions, in this case function with names
 prefixed with \verb|prop_|, taking a number of typed
-arguments, and returning a conditional. The property
-written in Haskell is also an Embeeded Domain specific
-language for properties.
+arguments, and returning a conditional is a small language.
+The property written in Haskell is also an Embedded Domain Specific
+Language for properties.
 
@@
 \begin{Code}
-Prelude Test.QuickCheck> quickCheck prop_reverse 
+Prelude Test.QuickCheck> quickCheck prop_reverse_twice
 +++ OK, passed 100 tests.
@@
 we execute our ESDL inside Haskell. The quickCheck function
-generates 100 test cases for our property, and exectutes
+generates 100 test cases for our property, and executes
 them on the fly. If they all hold, then the system prints
-a message reflecting this.
+a message reflecting this. The test cases are generated using
+the type class system -- QuickCheck gives specific types the
+power of test-case generation -- and the \verb|quickCheck| function
+uses this to generate random tests.
+
+Properties are useless unless they are falsify-able. As an examples
+of an incorrect property, consider this property for reverse.
+\begin{Code}
+prop_reverse xs ys = reverse xs ++ reverse ys == reverse (xs ++ ys)
+\end{Code}
+This is stating that the reverse of two distinct lists
+is the same as the reverse of both lists appended together.
+But this property is false.
+\begin{Code}
+Prelude Test.QuickCheck> quickCheck prop_reverse 
+FALSE!!!
+\end{Code}
 
 In turns out that this sort of mini-language is really useful in practice.
-
-((Go into my QC notes))
+Despite the simplicity of how Haskell is being used, the QuickCheck EDSL
+provided a way of thinking about and directly expressing properties.
+In the full QuickCheck EDSL has additional functionality, including
+the ability to generate random function arguments, the ability to control
+the distribution of the random test cases, and the ability to state pre-conditions
+to a property. From this language, several other implementations of
+these idea have been constructed. There is even a swedish company, ???,
+which sells a QuickCheck for Erlang, a language for large scale concurrency
+as found in telephone switches, and the language used by snapchat, the recent
+Facebook \$19 billion dollar purchase.
 

### 2014-03-13 paper.tex
More KL; starting the deep stuff.

@@
    Nothing == Nothing = True
-   _       == _       = False
+   \_       == \_       = False
 \end{Code}
@@
 
-Kansas Lava~\cite{Gill:13:TypesKansasLava} is a Haskell-hosted DSL developed by the PI
+Kansas Lava~\cite{Gill:13:TypesKansasLava} is a Haskell-hosted DSL
 that follows the Lava line of research.
@@
 
+\begin{figure}[!t]
+    \includegraphics[width=0.4\textwidth]{images/Counter.pdf}
+  \caption{{\tt counter} Schematic Kansas Lava parity counter}
+  \label{fig:counter-picture}
+\end{figure}
+
 We can simulate sequential circuits with the
@@
 function is finite. We use the \verb|Rep|
-constraint to signify that we can enumerate
+capability to signify that we can enumerate
 all possible representable values in a type,
@@
 
-\subsection{Observations of Embedeed DSLs}
+We can now use our clock squaring ROM at specific types,
+for example at 8-bit we can generate the follows.
+\begin{Code}
+GHCi> squareROM (toSeq [0,1..])        
+0 : 1 : 4 : 9 : 16 : 25 : 36 : 49 : 64 : 81 : 100 : 121 : 144 : 169 : 196 : 225 : 0 : ...
+\end{Code}
+
+This level of circuit specification has been used to great
+effect in many Lava and Lava-like languages. One notable
+instance is Hawk, a Lava-like EDSL which was used to specify
+the entire micro-architecture of the Pentium-Pro, including the
+super-scaler design, and register bypass capabilities.
+
+If DSLs are so powerful as an idiom for library design, then why have the taken over?
+As a means for expressing things that can be {\em simulated\/}, EDSLs are an invaluable
+design pattern. There are many, many examples, including ....
+
+\subsection{Deeply Embedded Domain Specific Language}
+
+But not everything is a simulation. What if we wanted to use an EDSL to express
+something that we want to run somewhere else, not inside the Haskell system?
+Can we use Lava to generate circuits, and run them on FPGAs? Can we use EDSL
+to generate code for embedded processors, or GPUs? Such an ability, to 
+synthesis external solutions, would be extremely useful. And we can extend
+the EDSL idiom to do so, with significant caveats. The remainder of this
+paper is about how we capture and offshore work from inside a EDSL, what
+this capability can be used for, and what the limitations are.
+
+\cursor{}
 
@@
 of provided functions, often called combinators, because they combine
-their arguments into terms inside the DSL lanuage.
+their arguments into terms inside the DSL language.
 
@@
   \caption{{\tt counter} Schematic and VHDL Generated by Kansas Lava}
-  \label{fig:counter-picture}
+  \label{fig:counter-pictureX}
 %  \vspace{-0.1in}

### 2014-03-13 paper.tex
Basic DESDL intro + first example

@@
 
-\subsection{Deeply Embedded Domain Specific Language}
-
-But not everything is a simulation. What if we wanted to use an EDSL to express
+Not everything is a simulation. What if we wanted to use an EDSL to express
 something that we want to run somewhere else, not inside the Haskell system?
@@
 to generate code for embedded processors, or GPUs? Such an ability, to 
-synthesis external solutions, would be extremely useful. And we can extend
+synthesis external solutions, would be extremely useful. We can extend
 the EDSL idiom to do so, with significant caveats. The remainder of this
@@
 
-\cursor{}
+\subsection{Deeply Embedded Domain Specific Language}
 
-As can be seen, EDSLs are simply a way of thinking about a library
+EDSLs are simply a way of thinking about a library
 of provided functions, often called combinators, because they combine
-their arguments into terms inside the DSL language.
+their arguments into terms inside the DSL language and types. In our
+Lava example above, the \verb|register| combinator takes an initial
+value, and a incoming stream of values, and gives the new stream,
+delayed by a single cycle, with the initial value occupying the initial
+cycle. Critically, \verb|register| is compositional; it combines
+smaller parts of the DSL to make larger solutions. If a DSL
+follows this composability carefully by design, an alternative implementation
+is possible.
 
-Compositionally
-Combining elements into more complex ones should be easy and natural.
-Abstraction
-The user shouldn’t have to know (or be allowed to exploit) the underlying implementation of your types.
-
-(((MORE))
-
-There are two flavors of EDSLs.
-The most common flavor are
-{\em DSLs that use a shallow embedding\/}, where values are computed with directly.
-The result of a computation in a shallow DSL is a value.
+The most common flavor of DSL is one  that uses a so-called shallow embedding, where values are computed with directly.
+The result of a computation in a shallow DSL is a value. All the examples so far are shallow.
 But there is another class of DSLs, 
 specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
-The result of a computation inside a deep DSL
+The result of a computation inside a Deeply Embedded DSL (Deep EDSL)
 is a structure, not a value, and this structure can be used to compute a value,
-or be cross-compiled before being evaluated.
+or be cross-compiled before being evaluated. Such ``Deep'' EDSLs
+follow the composability mantra pedantically, by design and mandate.
 
-This is an important distinction. Historically, EDSLs have been shallow,
-and as such are simply a ways of structuring an API to a library. Deep EDSLs
-have the ability to {\em stage\/} code, that is executing a program
+Historically, EDSLs have been shallow; simply a way of structuring an API to a library. 
+However, Deep EDSLs have the ability to {\em stage\/} code, that is executing a program
 can generate another program, much like the well-known YACC DSL,
@@
 generate valid output from.
-%% That sentence is a bit garbled.
+There is a growing number of Deep EDSLs, and a body of research around their
+form and limitations.
+The unifying theme is that Deep EDSLs can be pragmatic, productive and useful.
 
-The unifying theme is that embedded DSLs can
-be pragmatic, productive and useful.
+In this section, we will investigate the basic structure of Deep EDSL compared to Shallow EDSLs,
+and look at three pragmatic tricks for improving the usefulness of Deep EDSLs.
 
-\section{Deep Embeddings of DSLs}
+\subsection{Building a Deep EDSL}
 
-A deeply embedded DSL is a DSL than can have ???.
-To make this concrete, consider a DSL for arithmetic,
+A deeply embedded DSL is a DSL that exposes its own structure.
+Rather than functions operating on a datastructure (a shallow DSL),
+a deep DSL build a structure, and allows some secondary agent to
+provide interpretation of this structures.
+To make this idea concrete, consider a DSL for arithmetic,
 with addition, subtraction, multiplication, and constants.
 We want to be able to {\bf run\/} this DSL. For a shallow
-embedding this is trival - we just use the built in 
+embedding this is trivial - we just use the built in 
 arithmetic. A deep embedding is where things get
@@
 
-Now we overload the arithemtic to use this E datatype;
-in Haskell Num is our overloading for integeral arithmetic.
+Now we overload the arithmetic to use this E datatype;
+in Haskell Num is our overloading for integral arithmetic.
 
@@
 instance Num E where
+  fromInteger n = Lit n
   e1 + e2 = Add e1 e2
-  ...
-
+  e1 - e2 = Sub e1 e2
+  e1 * e2 = Mul e1 e2
 \end{Code}
@@
 
+This profound, and the key idea that makes deep embeddings work. We can written
+an expression, and extracted a tree of {\em what\/} to do, not a direct result.
 With deep embeddings, it is common to also
 write a run function, that computes the structure
-of a catured computation, given a simple value.
+of a captured computation, given a simple value.
 \begin{Code}
 run :: E -> Int
-run (...)
+run (Lit n) = n
+run (Add a b) = run a + run b
+run (Sub a b) = run a - run b
+run (Mul a b) = run a * run b
 \end{Code}
+
+\cursor{}
 

### 2014-03-13 paper.tex
Closing arithmetic

@@
 
+\begin{figure}[!t]
+  \centering
+        XXXX
+  \caption{Shallow and Deep Embedding of Arithmetic}
+  \label{fig:counter-pictureX}
+%  \vspace{-0.1in}
+\end{figure}
+
+Figure~\ref{fig:deep-dsls} illustrates the differences between shallow and deep DSLs,
+and how a deep embedding combined with a specific run function gives the same result.
+For a deep embedded DSL, the run function restores the capability of the shallow
+embedding, but another function takes the embedded structure, and uses in in some creative way.
+
+There are many places this design pattern can be used. One example is the specification
+of surface textures as functions; it is possible to export these into code executable
+on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
+up how fast a shallow embedding of the same operations would run.  There is nothing
+that is specific about Haskell, or even functional languages here. Indeed, the same
+ideas have been used in Java, for a VHDL generator. Haskell, with its powerful abstractions,
+allows deep DSLs to be more than just function calls, and almost feel like a straightforward
+shallow embedding.
+
+In order to make deep DSLs practical, there are three folklore tricks that are used.
+First, we can capture functions, by using dummy arguments. Second, we can observe loops,
+buy using observable sharing. And finally, we call observe imperative statements,
+by using normalization. We will overview all these tricks, before concluding
+with shortcoming and remaining challenges.
+
+\subsection{How to extract a deep embedding from a function}
+
 \cursor{}
-
-About running the code.
-
-About 3 main tricks; functions, recursive values, and statements.
-
-\subsection{How to extract a deep embedding from a Function}
 

### 2014-03-13 paper.tex
Starting the loop

@@
 
-There are many places this design pattern can be used. One example is the specification
-of surface textures as functions; it is possible to export these into code executable
-on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
-up how fast a shallow embedding of the same operations would run.  There is nothing
-that is specific about Haskell, or even functional languages here. Indeed, the same
-ideas have been used in Java, for a VHDL generator. Haskell, with its powerful abstractions,
-allows deep DSLs to be more than just function calls, and almost feel like a straightforward
-shallow embedding.
-
 In order to make deep DSLs practical, there are three folklore tricks that are used.
@@
 Expressing function calls in terms of constructors,  and
-building expression trees is a gimic. THere are entire
-systems build on the idea of building structures 
-in principaled ways, for example JHDL~\cite{..}, but
-we can do much more. With careful construction,
-we can capture function defintions,
-and other synatically structuruals,
+building expression trees is a useful, but by itself is a gimic. 
+With careful construction, we can capture function definitions,
+and other synaxtically structures,
 directly from a deep embedding. It is at this
@@
 on a different target becomes possible.
+Consider a simple function to add one to its argument.
 
@@
 \verb|E|, and returns a new \verb|E|. How can we capture
-this function.
-The trick is to invent a unique E, and pass it as the argument
+this function?
+The trick is to invent a unique E, and pass it as a (dummy) argument
 to \verb|f|.
@@
 
-This is remarkable. We're run a function with 
-a dummy argument (called the protypical argument)
+This is remarkable! We're run a function with 
+a dummy argument (called the prototypical argument)
 and extracted the body of the function.
 
-About where is used.
+There are many places this design pattern can be used. One example is the specification
+of surface textures as functions; it is possible to export these into code executable
+on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
+up how fast a shallow embedding of the same operations would run.  There is nothing
+that is specific about Haskell, or even functional languages here. Indeed, the same
+ideas have been used in Java, for a VHDL generator. Haskell, with its powerful abstractions,
+allows deep DSLs to almost feel like a straightforward shallow embedding.
 
@@
 If we attempt to build a deep embedding of Lava directly,
-we will get into a infinite cycle. In order to illustrate
+we will get into a infinite cycle of structures. In order to illustrate
 the challenge, we will build a deep embedding of Lava,
@@
 data Signal where
-  Register :: a -> Signal a                      -> Signal a
-  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal a
-  Var      :: String                             -> Signal a -- the trick
+  Register :: a -> Signal clk a                  -> Signal clk a
+  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal clk a
+  Var      :: String                             -> Signal clk a -- the Var trick
 
-mux2 :: ...
-mux2 = mux2
+mux2 :: Signal clk Bool -> (Signal a,Signal a) -> Signal a
+mux2 c (a,b) = Mux2 c (a,b)
 

### 2014-03-14 paper.tex
Starting conc.

@@
 
-In order to make deep DSLs practical, there are three folklore tricks that are used.
+In order to make deep DSLs practical, there are two folklore tricks that are used almost
+always used.
 First, we can capture functions, by using dummy arguments. Second, we can observe loops,
-buy using observable sharing. And finally, we call observe imperative statements,
-by using normalization. We will overview all these tricks, before concluding
-with shortcoming and remaining challenges.
+buy using some form of observable sharing. 
+%And finally, we call observe imperative statements, by using normalization. 
+%We will overview both these tricks, before concluding with shortcomings, extensions, and remaining challenges.
 
@@
 Expressing function calls in terms of constructors,  and
-building expression trees is a useful, but by itself is a gimic. 
-With careful construction, we can capture function definitions,
+building expression trees is a useful, but by itself is a gimmick. 
+However, with careful construction, we can also capture function definitions,
 and other synaxtically structures,
@@
 
-First we need a structure for our Lava Language.
+First we need a structure for our Lava Language. We define the
+functions use above, but give then a deep embedding, called \verb|Signal|.
 \begin{Code}
@@
 
-instance Signal Sig where {...}
-
 \end{Code}
-
-\subsection{How to spot an imperative}
-
-Sometimes, a list of actions is the best way to express what you want to do.
-In Haskell, the \verb|do|-notation is used to chain together imperative actions.
-To give an example,
-
-\section{Reification Tricks}
-
-The obvious questions are do this tricks used here scale,
-and what are the limitations? The trick has
-been used on may large examples, including
-generating large telemerty circuits, 
-and (( .. feldspar )). It is considered a
-stardard pattern in the functional programming
-community, analogoues to the OO patterns
-enumerated in the gang of four book~\cite{..}.
-The trick is made all the more appealing
-because we can use operator overloading.
-But the trick does has serious limitations.
-
-The basis of a Deep EDSL is one of constructiveness.
-The aim is to construct a structure, then
-use that structure that was previously implicit.
-Figure summarizes the state of the art with
-deeply embedded reification
-
-\begin{verbatim}
-Expressions             Natural Fit
-Functions               The trick
-local bindings          Yes, using observable sharing
-internal functions      Yes, using extension of OS
-do-statements           Yes, using monadic reification
-control flow            Not directly, can simulate
-\end{verbatim}
-
-The Deep EDSL trick breaks down on control flow,
-which is not constructive, but instead requires
-directly
-
-The process of extracting a structure from a deeply embedded ESDL
-is called reification.
-
- * running the description to get the AST
-
-\section{Use of Haskell’s type system for various things }
-
- * expression data type 
- * the phantom types trick 
- * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
- * usefulness of laziness 
- * smart constructors ? 
- * sharing ?
-
-%--------------------------------
-% CAREER12
-
-\section{Domain Specific Languages}
+Now, if we attempt to extract \verb|counter|, things go horribly wrong.
+\begin{Code}
+GHCi> counter (Var "restart") (Var "inc")
+((( LOOPING CODE ))))
+\end{Code}        
+What has happened is the recursive definitions are unrolling when we try reify the function,
+or more specifically, the body of counter is looping. At this point, the EDSL community was
+stymied. There was efforts to use monadic structure, where the loop was expressing using
+\verb|do|-notation~\cite{...}, making the loop an observable effect. There was an unsafe
+extension to observe a limited form of sharing, by circumventing part of the purity of Haskell,
+called observable sharing.
+There was also an extension of Haskell input/output mechanism that allowed loops to
+be observed indirect, called IO-based observable sharing. The net effect of all three
+mechanisms is that the observed tree is rendered as a graph with named edges.
 
@@
    \begin{minipage}{0.5\textwidth}
-    \centering
-    \includegraphics[width=0.8\textwidth]{images/Counter.pdf}
-  \end{minipage}\begin{minipage}{0.5\textwidth}
      \centering
@@
 
+Haskell at this point rescues complexity. Advanced type-system mechanisms, such has higher-kind type
+arguments, allow a structure to be either a tree or graph, depending on type-level instantiation. 
+Omitting here the details, the reified function is a tree with sharing,
+then translated into a graph with explicit sharing. The final result for our example is
+\begin{Code}
+GHCi> reify (counter (Var "restart") (Var "inc"))
+[(0,REGISTER False 1),
+ (...)
+]
+\end{Code}
+In this output, each upper-case constructors correspond to its deep-embedding constructor.
+A quick inspection shows that we have captured the circuit as given in Figure~\ref{counter-picture}.
+From this netlist-style structure, it is straightforward to generate VHDL. For the example
+of 4-bit number, the VHDL is given in Figure~\cite{counter-picutureX}.
+
+These two tricks (prototypical argument, IO-based observable sharing) are the technical fundamentals
+of Kansas Lava. On top of this base, and with help from Haskell type system, an entire ecosystem
+for circuit generation has been developed. The DSL idiom allows programmers to use high-level 
+abstraction, in Haskell, and generate efficient circuits. But not all is rosy; writing a Lava
+program is not the same as writing a Haskell program because of the limitations of Deep
+embeddings.
+
+\subsection{A deep embedding is only half a program}
+
+The basis of a Deep EDSL is one of constructiveness.
+Functional programming is about constructing {\em and destructing\/} values.
+Because of this, a deep embedding can not reify any pattern matching, 
+or even direct usage of if-then-else, and other control flow. We side-stepped this
+in Kansas Lava, for example by using a \verb|mux2| constructor, 
+which encodes choice.
+
+How much further can the idiom be pushed, if we need to be constructive?
+The result is surprising. We start with our three capabilities:
+\begin{itemize}
+\item Basic expressions can be captured, by constructing a tree that is an analog to our syntax.
+\item Functions can be captured, using the a fake unique argument.
+\item Local bindings can be observed using some form of observable sharing.
+\end{itemize}
+With these three comes and automatic forth capability.
+\begin{itemize}
+\item MACRO EXPAND
+\end{itemize}
+
+Table~\cite{tab:status} gives the
+
+The aim is to construct a structure, then
+use that structure that was previously implicit.
+Figure summarizes the state of the art with
+deeply embedded reification
+
+\begin{verbatim}
+Expressions             Natural Fit
+Functions               The trick
+local bindings          Yes, using observable sharing
+internal functions      Yes, using extension of OS
+do-statements           Yes, using monadic reification
+control flow            Not directly, can simulate
+\end{verbatim}
+
+The Deep EDSL trick breaks down on control flow,
+which is not constructive, but instead requires
+directly
+
+\cursor{}
+
+\subsection{How to spot an imperative}
+
+Sometimes, a list of actions is the best way to express what you want to do.
+In Haskell, the \verb|do|-notation is used to chain together imperative actions.
+To give an example,
+
+\section{Reification Tricks}
+
+The obvious questions are do this tricks used here scale,
+and what are the limitations? The trick has
+been used on may large examples, including
+generating large telemerty circuits, 
+and (( .. feldspar )). It is considered a
+stardard pattern in the functional programming
+community, analogoues to the OO patterns
+enumerated in the gang of four book~\cite{..}.
+The trick is made all the more appealing
+because we can use operator overloading.
+But the trick does has serious limitations.
+
+The process of extracting a structure from a deeply embedded ESDL
+is called reification.
+
+ * running the description to get the AST
+
+\section{Use of Haskell’s type system for various things }
+
+ * expression data type 
+ * the phantom types trick 
+ * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
+ * usefulness of laziness 
+ * smart constructors ? 
+ * sharing ?
+
+%--------------------------------
+% CAREER12
+
+\section{Domain Specific Languages}
+
 We can also {\em reify\/} the circuit, into
@@
 \end{document}
+
+% TODO: Something about code to generate DSL; automatic macros

### 2014-03-14 paper.tex
At end, and 4665 words.

@@
 
-Table~\cite{tab:status} gives the
+There are also extensions to the basic techniques. The principle once are:
+\begin{itemize}
+\item Internal function calls can captured as notes on a graph, 
+rather than directly inlined~\cite{...}. 
+This helps compilation of large programs, giving a basic separate compilation capability.
+\item \verb|do|-statement can be reified, by normalization~\cite{...}. This result, called monadic
+reification, is surprising. There are strong technical reasons to be believe monadic reification
+should be impossible. However the normalization refactors the constraining that, by themselves would
+be impossible to solve, and matches them up, 1-on-1, with a matching solution, allowing the whole
+\verb|do|-notation to be solved and reified.
+Monadic reification is a recent discovery, but has already been used in several Deep DSLs,
+including feldspar, and Sunroof.
+\item Control flow is problematic, and can not be used directly. However,
+there is a generalization of Haskell boolean that do allow deep embedding capture~\cite{boolean}.
+Using this library, a DSL with control flow can be constructed, but it needs to be explicit
+code, at the DSL level, using constructors.
+\end{itemize}
 
-The aim is to construct a structure, then
-use that structure that was previously implicit.
-Figure summarizes the state of the art with
-deeply embedded reification
+So where does this leave Deep DSLs? They are clearly a useful tool for the
+language implementor, but come with costs and limitations. How can we therefore
+push the state of the art, and allow more of the Haskell language to reified?
+There are two primary shortcoming.
+One we have discussed already: control flow and pattern matching remain a thorn in Deep DSLs.
 
-\begin{verbatim}
-Expressions             Natural Fit
-Functions               The trick
-local bindings          Yes, using observable sharing
-internal functions      Yes, using extension of OS
-do-statements           Yes, using monadic reification
-control flow            Not directly, can simulate
-\end{verbatim}
+Parametric polymorphism, one of the strengths of functional program, is the other
+issue for deep DSLs. We need a specific structure to represent what we have captured,
+and arbitrary polymorphism interferes with this. Current system sidestep this
+by always instantiate at a specific type, but this expensive because size of
+the captured program can expand exponentially.
+Polymorphism was the technical reason that it was thought that monadic reification
+would not work, but in that case it was side-stepped by normalization; this technique
+does not generalize to all polymorphism.
 
-The Deep EDSL trick breaks down on control flow,
-which is not constructive, but instead requires
-directly
-
-\cursor{}
-
-\subsection{How to spot an imperative}
-
-Sometimes, a list of actions is the best way to express what you want to do.
-In Haskell, the \verb|do|-notation is used to chain together imperative actions.
-To give an example,
-
-\section{Reification Tricks}
-
-The obvious questions are do this tricks used here scale,
-and what are the limitations? The trick has
-been used on may large examples, including
-generating large telemerty circuits, 
-and (( .. feldspar )). It is considered a
-stardard pattern in the functional programming
-community, analogoues to the OO patterns
-enumerated in the gang of four book~\cite{..}.
-The trick is made all the more appealing
-because we can use operator overloading.
-But the trick does has serious limitations.
-
-The process of extracting a structure from a deeply embedded ESDL
-is called reification.
-
- * running the description to get the AST
-
-\section{Use of Haskell’s type system for various things }
-
- * expression data type 
- * the phantom types trick 
- * Use of type classes (e.g. distinction of Seq and Comb in Signal) 
- * usefulness of laziness 
- * smart constructors ? 
- * sharing ?
-
-%--------------------------------
-% CAREER12
-
-\section{Domain Specific Languages}
-
-We can also {\em reify\/} the circuit, into
-a VHDL program. This is the key advantage and the
-primary purpose of Kansas Lava. For example,
-if we reify the counter with a width of 4 bits, we generate
-the idiomatic but useable VHDL
-listed in Figure~\ref{fig:counter-picture}.
-
-This use of a Haskell DSL for expressing circuits
-is all well and good and {\em structural\/}.
-But how can Kansas Lava be utilized to
-describe more general forms of computation and parallelism?
-Unfortunately at this point the model breaks down
-to some degree. Programs can be written
-that generate specific components, like ALUs,
-but computation is more challenging to express
-in Kansas Lava and other deep DSLs.
+Deep DSLs is the value-level way of extracting an expression, but there are others.
+Quaziquoting is another, at the syntactically level. Haskell comes with an extensive
+template system, called Template Haskell, that can and is used for DSLs.
+(....)
+Perhaps the future of Deep DSLs is some hybrid between expression generation
+and quazi-quoting, combining the best of both systems.
 

### 2014-03-14 paper.tex
Adding figures from other computer.

@@
 There are two fundamental types of Domain Specific Languages
-(Figure X).
+(Figure~\ref{fig:types-of-dsls}).
 %
@@
 with its own compiler or interpreter, and is often used in
-its own ecosystem. (Figure X, (1)) 
+its own ecosystem. (Figure \ref{fig:types-of-dsls}(1)) 
 All the examples mentioned so far fall
@@
 but leverage the host language to provide an existing
-eco-structure and initial semantics. It is this second
+eco-structure and initial semantics. 
+(Figure \ref{fig:types-of-dsls}, (2))
+It is this second
 class of DSLs we are interested in, and is the subject of
@@
 
-\begin{figure}
-
-\vskip 1in        
-((FIGURE ABOUT DSL))
-
+\begin{figure}[!t]
+  \centering        
+  \includegraphics[width=0.4\textwidth]{images/TypesOfDSLs.pdf}
+  \caption{Types of Domain Specific Languages}
+  \label{fig:types-of-dsls}
 \end{figure}
@@
   \centering        
-        XXXX
+  \includegraphics[width=0.6\textwidth]{images/DeepEmbedding.pdf}
   \caption{Shallow and Deep Embedding of Arithmetic}
-  \label{fig:counter-pictureX}
-%  \vspace{-0.1in}
+  \label{fig:deep-dsls}
 \end{figure}
@@
 \subsection{How to extract a deep embedding from a function}
-
-\cursor{}
 

### 2014-03-14 paper.tex
Fix page 1

@@
 
-\title{Embedded Domain Specific Languages inside Functional Languages}
+\title{Domain Specific Languages and Code Synthesis}
 \author{Andy Gill, University of Kansas}
@@
 
-A Domain Specific Language is a special purpose language,
+A Domain Specific Language (DSL) is a special purpose language,
 designed to encapsulate possible computations in a specific
@@
 
-There are two fundamental types of Domain Specific Languages
+There are two fundamental types of DSLs
 (Figure~\ref{fig:types-of-dsls}).
 %
-The first, like the SQL example, is a first class language,
+The first, like the SQL example, is when a DSL is a first class language,
 with its own compiler or interpreter, and is often used in
@@
 %
-The other class of Domain Specific Languages are languages
-embedded inside another hosting language. Such languages
+The other class of DSLs are languages
+embedded inside another hosting language(Figure \ref{fig:types-of-dsls}(2)). 
+Such languages
 can have the look and feel of being their own languages,

### 2014-03-14 paper.tex
Pages 2 - 5

@@
 sufficient to make this article self-contained. This section was
-adapted from the Haskell primer given in~\cite{?}.
+is an extended version the Haskell primer given by the author in~\cite{?}.
 
@@
 \verb|True| and \verb|False|, \verb|Int| is the type of machine-sized
-words, \verb|Double| is the type of double precision floating
+words, \verb|Double| is the type of double precision IEEE floating
 point values; and this list goes on in the same manner as
@@
 \end{Code}
-\verb|Nothing| is a verb|Maybe| of anything, \verb|Just|, with an argument,
+\verb|Nothing| is a \verb|Maybe| of anything, \verb|Just|, with an argument,
 is a \verb|Maybe| with the type of the argument. These constructors can be
 used to construct and deconstruct structures, but there is never any updating;
-all structures as immutable.
+all structures in Haskell are immutable.
 
@@
   Nothing == Nothing = True
-   \_       == \_       = False
+  _       == _       = False
 \end{Code}
 
-This states that for any type that can be testing for equality,
+This states that for any type that can be tested for equality,
 we can also check \verb|Maybe| at the same type. We take the \verb|Maybe|
@@
 which provide higher-level interfaces and abstractions for well-understood systems.
-
-We look at two examples of DSLs, one for automatically generating test cases for software testing,
+We now look at two examples of DSLs, one for automatically generating test cases for software testing,
 and a second for specifying hardware circuit behaviors.
@@
 that is a two reverses cancel each other out. 
-Here is the neat part -- \verb|prop_reverse_twice| is {\bf also\/} a
+Here is the neat part --- \verb|prop_reverse_twice| is {\bf also\/} a
 domain specific statement, and as such can also be considered
@@
 Language for properties.
-
 We can run our EDSL, using a function called \verb|quickCheck|:
@@
 
-Properties are useless unless they are falsify-able. As an examples
-of an incorrect property, consider this property for reverse.
+As an example of an incorrect property, consider this property for reverse.
 \begin{Code}
@@
 Prelude Test.QuickCheck> quickCheck prop_reverse 
-FALSE!!!
+Falsifiable, after 5 tests:
+[0]
+[2,-2]
 \end{Code}
@@
 provided a way of thinking about and directly expressing properties.
-In the full QuickCheck EDSL has additional functionality, including
+In the QuickCheck EDSL there is additional functionality, including
 the ability to generate random function arguments, the ability to control
@@
 to a property. From this language, several other implementations of
-these idea have been constructed. There is even a swedish company, ???,
-which sells a QuickCheck for Erlang, a language for large scale concurrency
-as found in telephone switches, and the language used by snapchat, the recent
-Facebook \$19 billion dollar purchase.
+these idea have been constructed. There is even a Swedish company, Quviq,
+which sells a QuickCheck for the concurrent programming language Erlang.
 
-\section{Example EDSL: Kansas Lava}\label{sec:KansasLava}
+\subsection{Example EDSL: Kansas Lava}\label{sec:KansasLava}
 
@@
 Hardware description languages and functional languages have
-long enjoyed a fruitful partnership.
+long enjoyed a fruitful partnership and
 {\bf Lava} is the name given to a class of Haskell DSLs
@@
 is one of recursive components communicating via synchronized streams.
-Kansas Lava has been deployed for the generation of high-performance circuits for telemetry decoders,
+Kansas Lava has been utilized for the generation of high-performance circuits for telemetry decoders,
 though the model used is general.
@@
 
-counter :: (Rep a, Num a, Clock clk, sig ~ Signal clk) => sig Bool -> sig Bool -> sig a
+counter :: (Rep a, Num a) => Signal Bool -> Signal Bool -> Signal a
 counter restart inc = loop
@@
 \begin{Code}
-funMap :: (Rep a, Rep b, Clock c, sig ~ Signal c) => (a -> Maybe b) -> sig a -> sig b
+funMap :: (Rep a, Rep b) => (a -> Maybe b) -> Signal a -> Signal b
 \end{Code}
@@
 \begin{Code}
-squareROM :: (Num a, Rep a, Clock c, sig ~ Signal c) => sig a -> sig a
+squareROM :: (Num a, Rep a) => Signal a -> Signal a
 squareROM = funMap (\ x -> return (x * x))
@@
 We can now use our clock squaring ROM at specific types,
-for example at 8-bit we can generate the follows.
+for example at 8-bit we can generate the following:
 \begin{Code}
-GHCi> squareROM (toSeq [0,1..])        
+GHCi> squareROM (toSeq [0,1..] :: Signal Word8)        
 0 : 1 : 4 : 9 : 16 : 25 : 36 : 49 : 64 : 81 : 100 : 121 : 144 : 169 : 196 : 225 : 0 : ...
@@
 As a means for expressing things that can be {\em simulated\/}, EDSLs are an invaluable
-design pattern. There are many, many examples, including ....
-
-Not everything is a simulation. What if we wanted to use an EDSL to express
+design pattern. 
+However, not everything is a simulation. What if we wanted to use an EDSL to express
 something that we want to run somewhere else, not inside the Haskell system?
@@
 
-\subsection{Deeply Embedded Domain Specific Language}
+\section{Deeply Embedded Domain Specific Languages}
 
@@
 Lava example above, the \verb|register| combinator takes an initial
-value, and a incoming stream of values, and gives the new stream,
+value, and an incoming stream of values, and gives the new stream,
 delayed by a single cycle, with the initial value occupying the initial
@@
 
-The most common flavor of DSL is one  that uses a so-called shallow embedding, where values are computed with directly.
+The most common flavor of DSL is one  that uses a so-called shallow embedding~(Figure~\ref{fig:types-of-dsls}(2a)), where values are computed with directly.
 The result of a computation in a shallow DSL is a value. All the examples so far are shallow.
 But there is another class of DSLs, 
-specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~\cite{Elliott:03:CompileDSEL-JFP}.
+specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~(Figure~\ref{fig:types-of-dsls}(2b)).~\cite{Elliott:03:CompileDSEL-JFP}.
 The result of a computation inside a Deeply Embedded DSL (Deep EDSL)
@@
 
-Historically, EDSLs have been shallow; simply a way of structuring an API to a library. 
+Historically, EDSLs have been shallow; simply a way of structuring an API for a library. 
 However, Deep EDSLs have the ability to {\em stage\/} code, that is executing a program
@@
 observe the structure of the computation.
-\begin{SemiCode}
+\begin{Code}
 GHCi> 1 + 2 * 3
 Mul (Add (Lit 1) (Lit 2)) (Lit 3)
-\end{SemiCode}
+\end{Code}
 
@@
 always used.
-First, we can capture functions, by using dummy arguments. Second, we can observe loops,
-buy using some form of observable sharing. 
+Using the first trick, we can capture functions, via dummy arguments. Using the second trick, we can observe loops,
+via some form of observable sharing. 
 %And finally, we call observe imperative statements, by using normalization. 
@@
   Lit :: Integer -> E
-  ...
+  Add :: E -> E -> E
+  Sub :: E -> E -> E
+  Mul :: E -> E -> E
   Var :: String -> E    -- new constructor
 \end{Code}
+
+We can now run our function directly, and see the result in our deep embedding, or
+pass in our \verb|Var| argument, and see the actual function.
 
@@
 on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
-up how fast a shallow embedding of the same operations would run.  There is nothing
+up how fast a implementation of the same operations would run.  There is nothing
 that is specific about Haskell, or even functional languages here. Indeed, the same
-ideas have been used in Java, for a VHDL generator. Haskell, with its powerful abstractions,
+ideas have been used in Java, for a VHDL generator\cite{...}. 
+Haskell, with its powerful abstractions,
 allows deep DSLs to almost feel like a straightforward shallow embedding.
@@
 data Signal where
-  Register :: a -> Signal clk a                  -> Signal clk a
-  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal clk a
-  Var      :: String                             -> Signal clk a -- the Var trick
+  Register :: a -> Signal a                      -> Signal a
+  Mux2     :: Signal Bool -> (Signal a,Signal a) -> Signal a
+  Lit      :: a                                  -> Signal a
+  Add      :: Signal a -> Signal a               -> Signal a
+  Var      :: String                             -> Signal  a -- the Var trick
 
-mux2 :: Signal clk Bool -> (Signal a,Signal a) -> Signal a
+instance Num a => Num (Signal a) where
+  a + b = Add a b
+
+mux2 :: Signal Bool -> (Signal a,Signal a) -> Signal a
 mux2 c (a,b) = Mux2 c (a,b)
-
-toSeq :: a -> Signal a
-toSeq = ...
 
@@
 GHCi> counter (Var "restart") (Var "inc")
-((( LOOPING CODE ))))
+Mux2 (Var "inc") (Add (Mux2 (Var "restart") (Lit 0,Register 0 (Mux2 (Var "inc") ...
 \end{Code}        
+The output tree is infinite.
 What has happened is the recursive definitions are unrolling when we try reify the function,

### 2014-03-14 paper.tex
Updated

@@
   \centering
-   \begin{minipage}{0.5\textwidth}
+   \begin{minipage}{0.6\textwidth}
      \centering
@@
   \end{minipage}
-  \caption{{\tt counter} Schematic and VHDL Generated by Kansas Lava}
-  \label{fig:counter-pictureX}
+  \caption{VHDL Generated by Kansas Lava for {\tt counter}}
+  \label{fig:counter-VHDL}
 %  \vspace{-0.1in}
@@
 
-Haskell at this point rescues complexity. Advanced type-system mechanisms, such has higher-kind type
+Haskell at this point rescues us from some complexity. Advanced type-system mechanisms, such has higher-kind type
 arguments, allow a structure to be either a tree or graph, depending on type-level instantiation. 
@@
 GHCi> reify (counter (Var "restart") (Var "inc"))
-[(0,REGISTER False 1),
- (...)
-]
+[(0,MUX2 1 (2,3)),
+ (1,VAR "inc"),
+ (2,ADD 3 4),
+ (3,MUX2 5 (6,7)),
+ (4,LIT 1),
+ (5,VAR "restart"),
+ (6,LIT 0),
+ (7,REGISTER 0 0)]
 \end{Code}
@@
 From this netlist-style structure, it is straightforward to generate VHDL. For the example
-of 4-bit number, the VHDL is given in Figure~\cite{counter-picutureX}.
+of 4-bit number, the VHDL is given in Figure~\ref{fig:counter-VHDL}.
 
@@
 
-\subsection{A deep embedding is only half a program}
+\section{A deep embedding is only half a program}
 
@@
 \begin{itemize}
-\item MACRO EXPAND
+\item The host language provides a built-in macro capability to the embedded language.
+Any part of Haskell (including control flow and pattern matching) can be used
+to {\em generate\/} the embedded language. 
 \end{itemize}
 
+\nonident
 There are also extensions to the basic techniques. The principle once are:
@@
 reification, is surprising. There are strong technical reasons to be believe monadic reification
-should be impossible. However the normalization refactors the constraining that, by themselves would
+should be impossible. However the normalization refactors the constrains that, by themselves would
 be impossible to solve, and matches them up, 1-on-1, with a matching solution, allowing the whole
@@
 Monadic reification is a recent discovery, but has already been used in several Deep DSLs,
-including feldspar, and Sunroof.
+including Feldspar\cite{..} and Sunroof\cite{..}.
 \item Control flow is problematic, and can not be used directly. However,
@@
 Using this library, a DSL with control flow can be constructed, but it needs to be explicit
-code, at the DSL level, using constructors.
+code, at the DSL level, using constructors. The usage is clumsy, but workable, and we should
+be able to do better.
 \end{itemize}
@@
 template system, called Template Haskell, that can and is used for DSLs.
-(....)
 Perhaps the future of Deep DSLs is some hybrid between expression generation
-and quazi-quoting, combining the best of both systems.
+and quazi-quoting, combining the best of both systems. (need stronger finish)
 

### 2014-03-14 paper.tex
Sent to Jim

@@
 \begin{figure}[!t]
+  \centering         
     \includegraphics[width=0.4\textwidth]{images/Counter.pdf}
@@
 smaller parts of the DSL to make larger solutions. If a DSL
-follows this composability carefully by design, an alternative implementation
+follows this composability carefully by design, an important alternative implementation
 is possible.
@@
 GHCi> 1 + 2 * 3
-Mul (Add (Lit 1) (Lit 2)) (Lit 3)
+Add (Lit 1) (Mul (Lit 2) (Lit 3))
 \end{Code}
@@
 However, with careful construction, we can also capture function definitions,
-and other synaxtically structures,
+and other syntactical structures,
 directly from a deep embedding. It is at this
@@
 -- Just running the function
-> f 4
+GHCi> f 4
 Add (Lit 4) (Lit 1)
 -- reifing the function, using our unique E ``Var''.
-> f (Var "x")
+GHCi> f (Var "x")
 Add (Var "x") (Lit 1)   -- reified version of the function
@@
 In this output, each upper-case constructors correspond to its deep-embedding constructor.
-A quick inspection shows that we have captured the circuit as given in Figure~\ref{counter-picture}.
+A quick inspection shows that we have captured the circuit as given in Figure~\ref{fig:counter-picture}.
 From this netlist-style structure, it is straightforward to generate VHDL. For the example
@@
 
-\nonident
+\noindent
 There are also extensions to the basic techniques. The principle once are:

### 2014-03-14 paper.tex
Edits to Section 1

@@
 \DefineVerbatimEnvironment{SemiCode}{Verbatim}{fontsize=\small,commandchars=\+\{\}}
+
+\hyphenation{MATLAB} % prevent breaking over lines
 
@@
 not think of herself as a programmer.)
-All these examples are use of domain specific languages.
+All these examples are uses of domain specific languages.
 
@@
 All the examples mentioned so far fall
-into this category. The primary difference between SQL and
-(say) Java is one of scope and focus, though sometimes
-DSLs grow to be as large are general purpose languages.
+into this category. The primary difference between SQL and,
+for instance, Java is one of scope and focus, though sometimes
+DSLs grow to be as large as general purpose languages.
 %
 The other class of DSLs are languages
-embedded inside another hosting language(Figure \ref{fig:types-of-dsls}(2)). 
+embedded in a host language(Figure \ref{fig:types-of-dsls}(2)). 
 Such languages
 can have the look and feel of being their own languages,
-but leverage the host language to provide an existing
-eco-structure and initial semantics. 
+but leverage the host language's existing
+ecosystem and initial semantics. 
 (Figure \ref{fig:types-of-dsls}, (2))

### 2014-03-14 paper.tex
Edits to Section 2

@@
 Haskell~\cite{Haskell98Book}, the premier pure functional programming language, is a great host for EDSLs
-because of flexible overloading, a powerful type system, and lazy semantics facilitating this.
+because of flexible overloading, a powerful type system, and lazy semantics.
 In this section, we give a terse
 introduction to Haskell, 
-sufficient to make this article self-contained. This section was
-is an extended version the Haskell primer given by the author in~\cite{?}.
+sufficient to make this article self-contained. This section
+is an extended version of the Haskell primer given by the author in~\cite{?}.
 
@@
 
-On top of these basic types, Haskell has two syntactical forms for expressing
+On top of these basic types, Haskell has two syntactic forms for expressing
 compound types.
@@
 So \verb|(Int,Bool)| is structure with both an \verb|Int| and a \verb|Bool| component.
-Second, lists have a syntactical shortcut, using square brackets.
+Second, lists have a syntactic shortcut, using square brackets.
 So \verb|[Int]| is a list of \verb|Int|.

### 2014-03-14 paper.tex
Pushing the bibtex file
Section 3 edits

@@
 customized to a specific problem domain.
-Using Haskell's concise syntax, Haskell specifically and the functional programming
-community in general have taken the ideas
-of EDSLs, which considerably lowered the costs of developing
-and maintaining a DSL, and developed many, many of DSL 
+EDSLs, by reusing the facilities and tools of the host language, considerably lower the cost of developing and maintaining a DSL.
+Benefiting from Haskell's concise syntax, the Haskell community, and the functional programming
+community in general, have taken the ideas
+of EDSLs and developed a large number of DSLs
 which provide higher-level interfaces and abstractions for well-understood systems.

### 2014-03-14 paper.tex
Added the references

--- 2014-03-14 paper.tex
@@
 \usepackage[paper=letterpaper,margin=1.0in,includehead=false,includefoot=false]{geometry}
+\usepackage{cite}
 
@@
 
-\hyphenation{MATLAB} % prevent breaking over lines
-
 \begin{document}
 
-\title{Domain Specific Languages and Code Synthesis}
+\title{Domain Specific Languages and Code Synthesis using Haskell}
 \author{Andy Gill, University of Kansas}
@@
 not think of herself as a programmer.)
-All these examples are uses of domain specific languages.
+All these examples are use of domain specific languages.
 
@@
 All the examples mentioned so far fall
-into this category. The primary difference between SQL and,
-for instance, Java is one of scope and focus, though sometimes
-DSLs grow to be as large as general purpose languages.
+into this category. The primary difference between SQL and
+(say) Java is one of scope and focus, though sometimes
+DSLs grow to be as large are general purpose languages.
 %
 The other class of DSLs are languages
-embedded in a host language(Figure \ref{fig:types-of-dsls}(2)). 
+embedded inside another hosting language(Figure \ref{fig:types-of-dsls}(2)). 
 Such languages
 can have the look and feel of being their own languages,
-but leverage the host language's existing
-ecosystem and initial semantics. 
+but leverage the host language to provide an existing
+eco-structure and initial semantics. 
 (Figure \ref{fig:types-of-dsls}, (2))
@@
 sufficient to make this article self-contained. This section was
-is an extended version the Haskell primer given by the author in~\cite{?}.
+is an extended version the Haskell primer given by the author in~\cite{Gill:11:Declarative}.
 
@@
 that is specific about Haskell, or even functional languages here. Indeed, the same
-ideas have been used in Java, for a VHDL generator\cite{...}. 
+ideas have been used in Java, for a VHDL generator\cite{Bellows:98:JHDL}. 
 Haskell, with its powerful abstractions,
@@
 stymied. There was efforts to use monadic structure, where the loop was expressing using
-\verb|do|-notation~\cite{...}, making the loop an observable effect. There was an unsafe
+\verb|do|-notation~\cite{Erkok:2000:Recursive-Monad},
+making the loop an observable effect. There was an unsafe
 extension to observe a limited form of sharing, by circumventing part of the purity of Haskell,
-called observable sharing.
+called observable sharing~\cite{Claessen:99:ObserveSharing}.
 There was also an extension of Haskell input/output mechanism that allowed loops to
-be observed indirect, called IO-based observable sharing. The net effect of all three
+be observed indirect, called IO-based observable sharing~\cite{Gill:09:TypeSafeReification}. 
+The net effect of all three
 mechanisms is that the observed tree is rendered as a graph with named edges.
@@
 \item Internal function calls can captured as notes on a graph, 
-rather than directly inlined~\cite{...}. 
+rather than directly inlined~\cite{Mainland:10:Nikola}. 
 This helps compilation of large programs, giving a basic separate compilation capability.
-\item \verb|do|-statement can be reified, by normalization~\cite{...}. This result, called monadic
+\item \verb|do|-statement can be reified, by normalization~\cite{Sculthorpe:13:ConstrainedMonad,Svenningsson:13:CompositionalMonadReification,Persson:11:GenericMonadicConstructs}.
+This result, called monadic
 reification, is surprising. There are strong technical reasons to be believe monadic reification
@@
 Monadic reification is a recent discovery, but has already been used in several Deep DSLs,
-including Feldspar\cite{..} and Sunroof\cite{..}.
+including Feldspar\cite{Axelsson:2010:DandI-Feldspar} and Sunroof\cite{Bracker:14:Sunroof}.
 \item Control flow is problematic, and can not be used directly. However,
-there is a generalization of Haskell boolean that do allow deep embedding capture~\cite{boolean}.
+there is a generalization of Haskell boolean that does allow deep embedding capture~\cite{hackage:boolean}.
 Using this library, a DSL with control flow can be constructed, but it needs to be explicit
@@
 
+\bibliography{paper}{}
+\bibliographystyle{plain}
+
 \end{document}

### 2014-03-14 paper.tex

--- 2014-03-14 paper.tex
@@
 
-\title{Domain Specific Languages and Code Synthesis}
+\title{Domain Specific Languages and Code Synthesis using Haskell}
 \author{Andy Gill, University of Kansas}
@@
 sufficient to make this article self-contained. This section
-is an extended version of the Haskell primer given by the author in~\cite{?}.
+is an extended version of the Haskell primer given by the author in~\cite{Gill:11:Declarative}.
 

### 2014-03-14 paper.tex
Final review

@@
 ecosystem and initial semantics. 
-(Figure \ref{fig:types-of-dsls}, (2))
+(Figure \ref{fig:types-of-dsls}(2))
 It is this second
@@
 a sub-language inside of Haskell itself.  This style
-of using functions, in this case function with names
+of using functions, in this case functions with names
 prefixed with \verb|prop_|, taking a number of typed
@@
 By running \verb|quickCheck| with our explicit and specific property,
-we execute our ESDL inside Haskell. The quickCheck function
+we execute our ESDL inside Haskell. The \verb|quickCheck| function
 generates 100 test cases for our property, and executes
@@
 the distribution of the random test cases, and the ability to state pre-conditions
-to a property. From this language, several other implementations of
+to a property. From this DSL, many other implementations of
 these idea have been constructed. There is even a Swedish company, Quviq,
@@
 
-If DSLs are so powerful as an idiom for library design, then why have the taken over?
+If DSLs are so powerful as an idiom for library design, then why have DSLs not taken over?
 As a means for expressing things that can be {\em simulated\/}, EDSLs are an invaluable
@@
 But there is another class of DSLs, 
-specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~(Figure~\ref{fig:types-of-dsls}(2b)).~\cite{Elliott:03:CompileDSEL-JFP}.
+specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~(Figure~\ref{fig:types-of-dsls}(2b)).
 The result of a computation inside a Deeply Embedded DSL (Deep EDSL)
 is a structure, not a value, and this structure can be used to compute a value,
-or be cross-compiled before being evaluated. Such ``Deep'' EDSLs
+or be cross-compiled before being evaluated~\cite{Elliott:03:CompileDSEL-JFP}. Such ``Deep'' EDSLs
 follow the composability mantra pedantically, by design and mandate.
@@
 
-Now, if we build expressions of type E, we can
+If we build expressions of type E, we can
 observe the structure of the computation.
@@
 which encodes choice.
-
-How much further can the idiom be pushed, if we need to be constructive?
+So, how much further can the idiom be pushed, if we need to be constructive?
 The result is surprising. We start with our three capabilities:
@@
 \end{itemize}
-With these three comes and automatic forth capability.
+With these three comes an automatic forth capability.
 \begin{itemize}
@@
 \noindent
-There are also extensions to the basic techniques. The principle once are:
+There are also extensions to the basic techniques. The principal ones are:
 \begin{itemize}
@@
 should be impossible. However the normalization refactors the constrains that, by themselves would
-be impossible to solve, and matches them up, 1-on-1, with a matching solution, allowing the whole
+be impossible to solve, and matches them up, 1-on-1, with a matching witness, allowing the whole
 \verb|do|-notation to be solved and reified.
@@
 Perhaps the future of Deep DSLs is some hybrid between expression generation
-and quazi-quoting, combining the best of both systems. (need stronger finish)
+and quazi-quoting, combining the best of both systems?
 

### 2014-03-14 paper.tex
an EDSL

@@
 
-As a first example of a EDSL, consider the challenge of writing test cases.
+As a first example of an EDSL, consider the challenge of writing test cases.
 Or more specifically, writing the {\em properties\/} that test cases need to satisfy.
@@
 the EDSL idiom to do so, with significant caveats. The remainder of this
-paper is about how we capture and offshore work from inside a EDSL, what
+paper is about how we capture and offshore work from inside an EDSL, what
 this capability can be used for, and what the limitations are.

### 2014-03-14 paper.tex
quazi -> quasi
Section 4.1

@@
 something that we want to run somewhere else, not inside the Haskell system?
-Can we use Lava to generate circuits, and run them on FPGAs? Can we use EDSL
+Can we use Lava to generate circuits, and run them on FPGAs? Can we use EDSLs
 to generate code for embedded processors, or GPUs? Such an ability, to 
@@
 A deeply embedded DSL is a DSL that exposes its own structure.
-Rather than functions operating on a datastructure (a shallow DSL),
-a deep DSL build a structure, and allows some secondary agent to
-provide interpretation of this structures.
+Rather than functions operating directly on values (a shallow DSL),
+a deep DSL builds a structure, then allows some secondary agent to
+provide interpretation of this structure.
 To make this idea concrete, consider a DSL for arithmetic,
@@
 
-This profound, and the key idea that makes deep embeddings work. We can written
-an expression, and extracted a tree of {\em what\/} to do, not a direct result.
+This is profound, and the key idea that makes deep embeddings work. We can write
+an expression and extract a tree of {\em what\/} to do, not a direct result.
 With deep embeddings, it is common to also
-write a run function, that computes the structure
-of a captured computation, given a simple value.
+write a run function, that computes the result
+of a captured computation.
 \begin{Code}
@@
 
-In order to make deep DSLs practical, there are two folklore tricks that are used almost
+In order to make deep DSLs practical, there are two folklore tricks that are almost
 always used.
-Using the first trick, we can capture functions, via dummy arguments. Using the second trick, we can observe loops,
+The first trick allows the capture of functions, via dummy arguments. The second trick can observe loops,
 via some form of observable sharing. 
@@
 Perhaps the future of Deep DSLs is some hybrid between expression generation
-and quazi-quoting, combining the best of both systems?
+and quasi-quoting, combining the best of both systems?
 

### 2014-03-14 paper.tex
Rest of 4

@@
 
-Expressing function calls in terms of constructors,  and
+Expressing function calls in terms of constructors and
 building expression trees is a useful, but by itself is a gimmick. 
@@
 First we need a structure for our Lava Language. We define the
-functions use above, but give then a deep embedding, called \verb|Signal|.
+functions used above, but give them a deep embedding, called \verb|Signal|.
 \begin{Code}
@@
 or more specifically, the body of counter is looping. At this point, the EDSL community was
-stymied. There was efforts to use monadic structure, where the loop was expressing using
+stymied. There were efforts to use monadic structure, where the loop was expressing using
 \verb|do|-notation~\cite{Erkok:2000:Recursive-Monad},
@@
 There was also an extension of Haskell input/output mechanism that allowed loops to
-be observed indirect, called IO-based observable sharing~\cite{Gill:09:TypeSafeReification}. 
+be observed indirectly, called IO-based observable sharing~\cite{Gill:09:TypeSafeReification}. 
 The net effect of all three
@@
 From this netlist-style structure, it is straightforward to generate VHDL. For the example
-of 4-bit number, the VHDL is given in Figure~\ref{fig:counter-VHDL}.
+of 4-bit numbers, the VHDL is given in Figure~\ref{fig:counter-VHDL}.
 
 These two tricks (prototypical argument, IO-based observable sharing) are the technical fundamentals
-of Kansas Lava. On top of this base, and with help from Haskell type system, an entire ecosystem
+of Kansas Lava. On top of this base, and with help from the Haskell type system, an entire ecosystem
 for circuit generation has been developed. The DSL idiom allows programmers to use high-level 

### 2014-03-14 paper.tex
Rest of paper edits

@@
 Functional programming is about constructing {\em and destructing\/} values.
-Because of this, a deep embedding can not reify any pattern matching, 
+Because of this, a deep embedding cannot reify any pattern matching, 
 or even direct usage of if-then-else, and other control flow. We side-stepped this
@@
 \item Basic expressions can be captured, by constructing a tree that is an analog to our syntax.
-\item Functions can be captured, using the a fake unique argument.
+\item Functions can be captured, using a fake unique argument.
 \item Local bindings can be observed using some form of observable sharing.
 \end{itemize}
-With these three comes an automatic forth capability.
+With these three comes an automatic fourth capability.
 \begin{itemize}
@@
 reification, is surprising. There are strong technical reasons to be believe monadic reification
-should be impossible. However the normalization refactors the constrains that, by themselves would
+should be impossible. However the normalization refactors the constraints that, by themselves, would
 be impossible to solve, and matches them up, 1-on-1, with a matching witness, allowing the whole
@@
 including Feldspar\cite{Axelsson:2010:DandI-Feldspar} and Sunroof\cite{Bracker:14:Sunroof}.
-\item Control flow is problematic, and can not be used directly. However,
+\item Control flow is problematic, and cannot be used directly. However,
 there is a generalization of Haskell boolean that does allow deep embedding capture~\cite{hackage:boolean}.
@@
 issue for deep DSLs. We need a specific structure to represent what we have captured,
-and arbitrary polymorphism interferes with this. Current system sidestep this
-by always instantiate at a specific type, but this expensive because size of
+and arbitrary polymorphism interferes with this. Current systems sidestep this
+by always instantiating at a specific type, but this is expensive because the size of
 the captured program can expand exponentially.
@@
 
-Deep DSLs is the value-level way of extracting an expression, but there are others.
-Quaziquoting is another, at the syntactically level. Haskell comes with an extensive
-template system, called Template Haskell, that can and is used for DSLs.
+Deep DSLs is a value-level way of extracting an expression, but there are others.
+Quasi-quoting is another, at the syntactic level. Haskell comes with an extensive
+template system, called Template Haskell, that is used for DSLs.
 Perhaps the future of Deep DSLs is some hybrid between expression generation

### 2014-04-04 Example.hs
Adding test of an example

@@ -1,0 +1,22 @@
+{-# LANGUAGE GADTs #-}
+
+data Expr where
+  Lit :: Integer -> Expr
+  Add :: Expr -> Expr -> Expr
+  Sub :: Expr -> Expr -> Expr
+  Mul :: Expr -> Expr -> Expr
+  Var :: String -> Expr    -- new constructor
+  deriving Show
+
+
+f :: Expr -> Expr
+f x = x + 1
+
+g :: Expr -> Expr -> Expr
+g x y = x * x + y + 2
+
+instance Num Expr where
+  fromInteger n = Lit n
+  e1 + e2 = Add e1 e2
+  e1 - e2 = Sub e1 e2
+  e1 * e2 = Mul e1 e2

### 2014-04-04 paper.tex
Fixing the paper

@@
 to the database engine.
-To pick a concrete example,
-consider the act of trying to list a dynamically updated leader-board
-for an online programming contest:
-\begin{Code}
-SELECT ROUND(SUM(s.Score)) as ss, t.TeamName FROM Solution s -- an aggregate score and team name
-   LEFT JOIN Team t ON SolutionTeam = TeamId                 -- where the team has the correct id
-   GROUP BY s.SolutionTeam                                   -- grouped by team name
-   ORDER BY ss DESC                                          -- ordered by score
-   LIMIT 20                                                  -- returning the first 20
-\end{Code}
-In a handful on lines, this query performs a complex
-database search, and some computation, finding
-the names and aggregate scores of the top 20 teams.
 
@@
 %
-The first, like the SQL example, is when a DSL is a first class language,
+The first is when a DSL is a first class language,
 with its own compiler or interpreter, and is often used in
@@
 All the examples mentioned so far fall
-into this category. The primary difference between SQL and,
+into this category. The primary difference between the SQL DSL and,
 for instance, Java is one of scope and focus, though sometimes
@@
 The other class of DSLs are languages
-embedded in a host language(Figure \ref{fig:types-of-dsls}(2)). 
+embedded in a host language (Figure \ref{fig:types-of-dsls}(2)). 
 Such languages
-can have the look and feel of being their own languages,
+can have the look and feel of being their own language,
 but leverage the host language's existing
@@
 
-Polymorphic values, which are analogous to the type \verb|Object| in Java,
-or \verb|void*| pointers in C, are expressed using lower-case letters.
+Polymorphic values are expressed using lower-case letters.
+and play a similar role 
+\verb|void*| pointers in C
+and polymorphic arguments in the Java generics facility.
 These polymorphic values can have constraints expressed over them,
 using the Haskell equivalent of an object hierarchy.
-Finally, a Haskell function that takes a list, and returns a list
-is written as using an arrow: \verb|[a] -> [a]|.
+
+Finally, a function is written using an arrow from 
+argument type to result type.
+So, in Haskell, a function that takes a list and returns a list
+is written as using: \verb|[a] -> [a]|.
 
@@
 \item The second line says that an empty list is already sorted.
-\item The remaining lines state that a (non-empty) list can be
+\item The remaining lines state that a non-empty list can be
 sorted by taking the first and rest of the list (called \verb|x| and \verb|xs|, respectively),
@@
   Nothing == Nothing = True
-  _       == _       = False
+  X       == X       = False
 \end{Code}
@@
 we can also check \verb|Maybe| at the same type. We take the \verb|Maybe|
-apart, using pattern matching on \verb|Just|, to check the internal value.a
+apart, using pattern matching on \verb|Just|, to check the internal value.
 
-In Haskell, Side-effects such as writing to the screen
+In Haskell, side-effects such as writing to the screen
 or reading the keyboard are described using a \verb|do|-notation, for example:
@@
 customized to a specific problem domain.
-EDSLs, by reusing the facilities and tools of the host language, considerably lower the cost of developing and maintaining a DSL.
+EDSLs, by reusing the facilities and tools of the host language, considerably lower the cost of both
+developing and maintaining a DSL.
 Benefiting from Haskell's concise syntax, the Haskell community, and the functional programming
@@
 The property written in Haskell is also an Embedded Domain Specific
-Language for properties.
-We can run our EDSL, using a function called \verb|quickCheck|:
+Language for properties, called QuickCheck~\cite{Claessen:00:QuickCheck}.
+We can run our EDSL, using a function also called \verb|quickCheck|:
 \begin{Code}
@@
 modern programming language with the same name, was based
-on relations, not functions, and was inspired by
+on relations, which was in turn inspired by
 the seminal work in $\mu$FP~\cite{Sheeran:84:muFP}.
@@
 GHCi> toSeq (cycle [True,False,False])
-T : F : F : T : F : F : T : F : F : ...
+True : False : False : True : False : False : True : False : False : ...
 GHCi> counter low (toSeq (cycle [True,False,False]))
@@
 effect in many Lava and Lava-like languages. One notable
-instance is Hawk, a Lava-like EDSL which was used to specify
+instance is Hawk~\cite{Matthews:1998:Hawk}, a Lava-like EDSL which was used to specify
 the entire micro-architecture of the Pentium-Pro, including the
@@
 
-If DSLs are so powerful as an idiom for library design, then why have DSLs not taken over?
+Now,if DSLs are so powerful as an idiom for library design, then why have DSLs not taken over?
 As a means for expressing things that can be {\em simulated\/}, EDSLs are an invaluable
@@
 of provided functions, often called combinators, because they combine
-their arguments into terms inside the DSL language and types. In our
+their arguments into terms inside the DSL language. In our
 Lava example above, the \verb|register| combinator takes an initial
@@
 specifically {\em DSLs that use a deep embedding\/} build an abstract syntax tree~(Figure~\ref{fig:types-of-dsls}(2b)).
-The result of a computation inside a Deeply Embedded DSL (Deep EDSL)
+The result of a computation inside a deeply Embedded DSL (deep EDSL)
 is a structure, not a value, and this structure can be used to compute a value,
-or be cross-compiled before being evaluated~\cite{Elliott:03:CompileDSEL-JFP}. Such ``Deep'' EDSLs
+or be cross-compiled before being evaluated~\cite{Elliott:03:CompileDSEL-JFP}. Such ``deep'' EDSLs
 follow the composability mantra pedantically, by design and mandate.
@@
 Historically, EDSLs have been shallow; simply a way of structuring an API for a library. 
-However, Deep EDSLs have the ability to {\em stage\/} code, that is executing a program
+However, deep EDSLs have the ability to {\em stage\/} code, that is executing a program
 can generate another program, much like the well-known YACC DSL,
@@
 generate valid output from.
-There is a growing number of Deep EDSLs, and a body of research around their
+There is a growing number of deep EDSLs, and a body of research around their
 form and limitations.
-The unifying theme is that Deep EDSLs can be pragmatic, productive and useful.
+The unifying theme is that deep EDSLs can be pragmatic, productive and useful.
 
-In this section, we will investigate the basic structure of Deep EDSL compared to Shallow EDSLs,
-and look at three pragmatic tricks for improving the usefulness of Deep EDSLs.
+In this section, we will investigate the basic structure of deep EDSL compared to Shallow EDSLs,
+and look at three pragmatic tricks for improving the usefulness of deep EDSLs.
 
@@
 
-A deeply embedded DSL is a DSL that exposes its own structure.
+A deeply embedded DSL is a DSL that exposes its own composition and structure.
 Rather than functions operating directly on values (a shallow DSL),
@@
 \begin{Code}
-data E where
- Lit :: Integer -> E
- Add :: E -> E -> E
- Sub :: E -> E -> E
- Mul :: E -> E -> E
+data Expr where
+ Lit :: Integer -> Expr
+ Add :: Expr -> Expr -> Expr
+ Sub :: Expr -> Expr -> Expr
+ Mul :: Expr -> Expr -> Expr
  deriving Eq
@@
 Now we overload the arithmetic to use this E datatype;
-in Haskell Num is our overloading for integral arithmetic.
+in Haskell \verb|Num| is our overloading for integral arithmetic.
 
 \begin{Code}
-instance Num E where
+instance Num Expr where
   fromInteger n = Lit n
@@
 \begin{Code}
-GHCi> 1 + 2 * 3
+GHCi> 1 + 2 * 3 :: Expr
 Add (Lit 1) (Mul (Lit 2) (Lit 3))
@@
 \begin{Code}
-run :: E -> Int
+run :: Expr -> Integer
 run (Lit n)   = n
@@
 
-In order to make deep DSLs practical, there are two folklore tricks that are almost
+In order to make deep DSLs practical, there are two additional tricks in the DSL folklore that are almost
 always used.
@@
 
-f :: E -> E
+f :: Expr -> Expr -> Expr
 f x = x + 1
@@
 Here we have a function that acts over our new type
-\verb|E|, and returns a new \verb|E|. How can we capture
+\verb|Expr|, and returns a new \verb|Expr|. How can we capture
 this function?
-The trick is to invent a unique E, and pass it as a (dummy) argument
+The trick is to invent a unique \verb|Expr|, and pass it as a (dummy) argument
 to \verb|f|.
@@
 \begin{Code}
-data E where
-  Lit :: Integer -> E
-  Add :: E -> E -> E
-  Sub :: E -> E -> E
-  Mul :: E -> E -> E
-  Var :: String -> E    -- new constructor
+data Expr where
+  Lit :: Integer -> Expr
+  Add :: Expr -> Expr -> Expr
+  Sub :: Expr -> Expr -> Expr
+  Mul :: Expr -> Expr -> Expr
+  Var :: String -> Expr    -- new constructor
 \end{Code}
@@
 Add (Lit 4) (Lit 1)
--- reifing the function, using our unique E ``Var''.
+-- reifing the function, using our unique Var.
 GHCi> f (Var "x")
@@
 
+This idea scales to multi-argument functions. Consider \verb|g|:
+
+\begin{Code}
+
+g :: Expr -> Expr -> Expr
+g x y = x * x + y + 2
+
+\end{Code}
+
+Given two argument protoypical arguments to \verb|g| will capture the function.
+
+\begin{Code}
+GHCi> g (Var "x") (Var "y")
+Add (Add (Mul (Var "x") (Var "x")) (Var "y")) (Lit 2)
+\end{Code}
+
 There are many places this design pattern can be used. One example is the specification
@@
 on GPUs, simultaneously lifting the abstractions used to write textures, and speeding
-up how fast a implementation of the same operations would run.  There is nothing
+up how fast an implementation of the same operations would run.  There is nothing
 that is specific about Haskell, or even functional languages here. Indeed, the same
@@
 
-\subsection{How to spot a loop}
+\subsection{How to Spot a Loop}
 
@@
 
+register :: a -> Signal a -> Signal a
+register d s = Register d s
+
 \end{Code}
@@
      \centering
-\footnotesize\begin{Code}[fontsize=\tiny]
+\footnotesize\begin{Code}[fontsize=\small]
 entity counter is
@@
 Using this library, a DSL with control flow can be constructed, but it needs to be explicit
-code, at the DSL level, using constructors. The usage is clumsy, but workable, and we should
-be able to do better.
+code, at the DSL level, using constructors. 
+The \verb|mux2| function used previously is a simplification of this idea.
+The usage is clumsy, but workable, and we should be able to do better.
 \end{itemize}
 
-So where does this leave Deep DSLs? They are clearly a useful tool for the
+So where does this leave Deep DSLs? They are clearly a useful design pattern for the
 language implementor, but come with costs and limitations. How can we therefore
@@
 Polymorphism was the technical reason that it was thought that monadic reification
-would not work, but in that case it was side-stepped by normalization; this technique
+was not possible, but in that case it was side-stepped by normalization; this technique
 does not generalize to all polymorphism.
 
-Deep DSLs is a value-level way of extracting an expression, but there are others.
-Quasi-quoting is another, at the syntactic level. Haskell comes with an extensive
-template system, called Template Haskell, that is used for DSLs.
-Perhaps the future of Deep DSLs is some hybrid between expression generation
-and quasi-quoting, combining the best of both systems?
+Deep DSLs is a value-level way of extracting an expression, but there are ways of
+extracting expressions.
+Quasi-quoting is another mechanism for extracting expressions, but at the syntactic level. 
+Haskell comes with an extensive template system, called Template Haskell\~cite{Sheard:02:metahaskell}, 
+that is often used for DSLs. There is a sense of unease with such solutions, however, much
+in the same way the C pre-processor is used, but not considered elegant. The principal issue
+is that the syntax of Haskell is huge, perhaps 100 syntactical terms. An expression-based
+solution, such as a deep embedding, can avoid the need to re-write front translations.
+Quasi-quoting has one important advantage, specifically it can cope with control flow,
+and deconstruction of values. So perhaps the future of deep DSLs is some hybrid between
+expression generation and quasi-quoting, combining the best of both systems.
 

### 2014-04-07 paper.tex
Fixing typo that wc used
Fixing typo with cite

@@
   Nothing == Nothing = True
-  X       == X       = False
+  _       == _       = False
 \end{Code}
@@
 Quasi-quoting is another mechanism for extracting expressions, but at the syntactic level. 
-Haskell comes with an extensive template system, called Template Haskell\~cite{Sheard:02:metahaskell}, 
+Haskell comes with an extensive template system, called Template Haskell~\cite{Sheard:02:metahaskell}, 
 that is often used for DSLs. There is a sense of unease with such solutions, however, much

### 2014-04-07 Main.hs
Adding paper after conversion

@@ -21,6 +21,156 @@ main = withCurlDo $ do
               , identifier t `Set.member` cs
               ]
 
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+<<<<<<< Local Changes
+
+     let alph a b = identifier a `compare` identifier b
+
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph ts
+=======
+
+     let alph a b = identifier a `compare` identifier b
+
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+
+     let alph a b = identifier a `compare` identifier b
+
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
+     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
+>>>>>>> External Changes
+=======
+     let alph a b = identifier a `compare` identifier b
[…]

### 2014-04-10 Main.hs
Fix bad checkin

@@ -21,156 +21,6 @@ main = withCurlDo $ do
               , identifier t `Set.member` cs
               ]
 
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-<<<<<<< Local Changes
-
-     let alph a b = identifier a `compare` identifier b
-
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph ts
-=======
-
-     let alph a b = identifier a `compare` identifier b
-
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-
-     let alph a b = identifier a `compare` identifier b
-
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
-     writeFile "paper.bib" $ unlines $ map F.entry $ sortBy alph $ ts
->>>>>>> External Changes
-=======
-     let alph a b = identifier a `compare` identifier b
[…]
